---
title: "TetraProject_DataAnalysis"
output: html_document
date: "2026-08-20"
---

# Effect of nutrients and predation on T. pyriformis thermal performance

loading libraries
```{r, message=FALSE}
library(tidyr)
library(dplyr)
library(ggplot2)
library(lme4)
library(emmeans)
library(rTPC)
library(nls.multstart)
library(boot)
library(car)
library(broom)
library(purrr)
library(patchwork)
library(forcats)
library(mgcv)
library(forcats)
```

loading data
```{r, results='hide'}
data<-read.csv(file="data.csv", header=TRUE)
str(data)
data$Nutrients<-factor(data$Nutrients) #assigning factors
data$Essay<-factor(data$Essay)
data$Predation<-factor(data$Predation)
data$Cat<-factor(data$Cat)
data$density<-data$Cells/3
```

### Pairwise comparations across treatments  
Statistical model fitting and comparation of each treatment across temperatures for growth rate
```{r}
#Starting with growth rate
mod_r <- gam(r ~ 
             Nutrients * Predation + Essay+ 
             s(Temp, by = interaction(Nutrients, Predation), k = 6),
           random = list(replicate = ~1),
           data = data,
           method = "REML")

summary(mod_r)

mod_r <- gam(r ~ 
             Nutrients * Predation + #we removed essay as it does not seemed to significantly explain anything
             s(Temp, by = interaction(Nutrients, Predation), k = 6),
           random = list(replicate = ~1),
           data = data,
           method = "REML")

summary(mod_r)


## Pairwise comparisons 
temps <- sort(unique(data$Temp))

emm <- emmeans(
 mod_r,
  ~ Nutrients * Predation | Temp,
  at = list(Temp = temps)
)

nutr_effect_r <- pairs(  #effect of nutrients across predation levels
  emm,
  by = c("Temp", "Predation"),
  adjust = "fdr"
)
nutr_effect_r 

pred_effect_r <- pairs(  #effect of nutrients across predation levels
  emm,
  by = c("Temp", "Nutrients"),
  adjust = "fdr"
)

pred_effect_r
```

```{r}
#Starting with density
mod_density <- gam(density ~ 
             Nutrients * Predation + Essay+
             s(Temp, by = interaction(Nutrients, Predation), k = 6),
           random = list(replicate = ~1),
           data = data,
           method = "REML")

summary(mod_density)

mod_density <- gam(density ~ 
             Nutrients * Predation+ # we removed essay as it does not seems to explain much 
             s(Temp, by = interaction(Nutrients, Predation), k = 6),
           random = list(replicate = ~1),
           data = data,
           method = "REML")

summary(mod_density)

## Pairwise comparisons 
temps <- sort(unique(data$Temp))

emm_density <- emmeans(
  mod_density,
  ~ Nutrients * Predation | Temp,
  at = list(Temp = temps)
)

nutr_effect_density <- pairs(  #effect of nutrients across predation levels
  emm_density,
  by = c("Temp", "Predation"),
  adjust = "fdr"
)

nutr_effect_density

pred_effect_density <- pairs(  #effect of nutrients across predation levels
  emm_density,
  by = c("Temp", "Nutrients"),
  adjust = "fdr"
)

pred_effect_density
```

Building a table
```{r}
nutr_table_density <- as.data.frame(nutr_effect_density) %>% # turning into data frame
  select(Temp, Predation, contrast, estimate, SE, t.ratio, p.value)

pred_table_density <- as.data.frame(pred_effect_density) %>% # turning into data frame
  select(Temp, Nutrients, contrast, estimate, SE, t.ratio, p.value)

nutr_table_density <- as.data.frame(nutr_table_density) %>%
  mutate(
    Effect = "Nutrients",
    Condition = paste("Predation =", Predation)
  ) %>%
  select(Effect, Temp, Condition, contrast, estimate, SE, t.ratio, p.value)

pred_table <- as.data.frame(pred_table_density) %>%
  mutate(
    Effect = "Predation",
    Condition = paste("Nutrients =", Nutrients)
  ) %>%
  select(Effect, Temp, Condition, contrast, estimate, SE, t.ratio, p.value)

final_table_density <- bind_rows(nutr_table_density, pred_table_density)

final_table_density <- final_table_density %>% # renaming some variables 
  select(-c(Effect))%>%
  rename(
    Temperature = Temp,
    Contrast = contrast,
    Estimate = estimate,
    SE = SE,
    t_value = t.ratio,
    p_value = p.value)%>%
  mutate(
    significance = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01  ~ "**",
      p_value < 0.05  ~ "*",
      TRUE ~ "ns")
  )


final_table_density<- final_table_density %>%
  mutate(
    significance = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01  ~ "**",
      p_value < 0.05  ~ "*",
      TRUE ~ "ns"
    )
  )


final_table_density

write.csv(final_table_density, "pairwise_comparisons_density.csv", row.names = FALSE)
```

Same for growth rate
```{r}
nutr_table_r <- as.data.frame(nutr_effect_r) %>% # turning into data frame
  select(Temp, Predation, contrast, estimate, SE, t.ratio, p.value)

pred_table_r <- as.data.frame(pred_effect_r) %>% # turning into data frame
  select(Temp, Nutrients, contrast, estimate, SE, t.ratio, p.value)

nutr_table_r <- as.data.frame(nutr_table_r) %>%
  mutate(
    Effect = "Nutrients",
    Condition = paste("Predation =", Predation)
  ) %>%
  select(Effect, Temp, Condition, contrast, estimate, SE, t.ratio, p.value)

pred_table <- as.data.frame(pred_table_r) %>%
  mutate(
    Effect = "Predation",
    Condition = paste("Nutrients =", Nutrients)
  ) %>%
  select(Effect, Temp, Condition, contrast, estimate, SE, t.ratio, p.value)

final_table_r <- bind_rows(nutr_table_r, pred_table_r)

final_table_r <- final_table_r %>% # renaming some variables 
  select(-c(Effect))%>%
  rename(
    Temperature = Temp,
    Contrast = contrast,
    Estimate = estimate,
    SE = SE,
    t_value = t.ratio,
    p_value = p.value)%>%
  mutate(
    significance = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01  ~ "**",
      p_value < 0.05  ~ "*",
      TRUE ~ "ns")
  )


final_table_r<- final_table_r %>%
  mutate(
    significance = case_when(
      p_value < 0.001 ~ "***",
      p_value < 0.01  ~ "**",
      p_value < 0.05  ~ "*",
      TRUE ~ "ns")
  )

final_table_r

write.csv(final_table_r, "pairwise_comparisons_r.csv", row.names = FALSE)
```
## TPC considering all treatments
We build two reference curves to include in the plots of growth rate and density
```{r}
data$T<-data$Temp+273

d<-data

start_vals <- get_start_vals(d$T, d$r, model_name = 'sharpeschoolhigh_1981')

# Sharpe Schoolfield high model
fit_schoolfield_resp<-nls_multstart(r~sharpeschoolhigh_1981(temp = T, r_tref, e, eh, th, tref = 293),
data = d,
iter = c(3,3,3,3),
start_lower = start_vals - 10,
start_upper = start_vals + 10,
lower = get_lower_lims(d$T, d$r, model_name = 'sharpeschoolhigh_1981'),
upper = get_upper_lims(d$T, d$r, model_name = 'sharpeschoolhigh_1981'),
supp_errors = 'Y',
convergence_count = FALSE) 

# Creating predictions
new_pred_r <- data.frame(T = seq(min(d$T-5), max(d$T+5), length.out=100))
new_pred_r$pred <- predict(fit_schoolfield_resp, newdata = new_pred_r)

# Predation prediction with bootstraping interval confidences
gen_plot_r<-ggplot() +
  geom_line(aes(T-273, pred), new_pred_r, col = 'blue') +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       y = 'Respiration rates',
       title = 'Growth rate with low nutrients and no predation')+
  ylim(0, 9)

gen_plot_r

## Curve for density
data$T<-data$Temp+273

start_vals <- get_start_vals(d$T, d$density, model_name = 'sharpeschoolhigh_1981')

# Sharpe Schoolfield high model
fit_schoolfield_resp<-nls_multstart(density~sharpeschoolhigh_1981(temp = T, r_tref, e, eh, th, tref = 293),
data = d,
iter = c(3,3,3,3),
start_lower = start_vals - 10,
start_upper = start_vals + 10,
lower = get_lower_lims(d$T, d$density, model_name = 'sharpeschoolhigh_1981'),
upper = get_upper_lims(d$T, d$density, model_name = 'sharpeschoolhigh_1981'),
supp_errors = 'Y',
convergence_count = FALSE) 

# Creating predictions
new_pred_density <- data.frame(T = seq(min(d$T-5), max(d$T+5), length.out=100))
new_pred_density$pred <- predict(fit_schoolfield_resp, newdata = new_pred_density)


# Predation prediction with bootstraping interval confidences
gen_plot_density<-ggplot() +
  geom_line(aes(T-273, pred), new_pred_density , col = 'blue') +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       y = 'Respiration rates',
       title = 'Growth rate with low nutrients and no predation')
#+
 # ylim(0, 9)

gen_plot_density
```
## Population growth rates (r) across nutrient and predation treatments and temperatures with TPC
```{r}
sum_pred_r<-data %>%
  group_by(Temp, Nutrients, Predation) %>%
  summarise(mean=mean(r), sd=sd(r), #summarizing abundance 
            n=n()) %>% #summarizing richness
  mutate(se=sd/sqrt(n))

sum_pred_r

pd <- position_dodge(width = 0.85)

plot_r<-ggplot() + #calling ggplot
  geom_point(data=sum_pred_r, aes(x=Temp, y=mean, color=Nutrients, shape=Predation, group = interaction(Nutrients, Predation)), 
             size = 2.5, position = pd)+
  geom_errorbar(data=sum_pred_r, aes(x=Temp, ymin=mean-se, ymax=mean+se, group = interaction(Nutrients, Predation), color=Nutrients),  
               size = 0.6, width = 0.2, alpha = 0.6, position = pd)+
 # geom_point(data=data, aes(x=Temp, y=r, color=Nutrients, shape=Predation, group = interaction(Nutrients, Predation)),
          #     size = 1, position = pd, alpha=0.2)+
   geom_line(aes(T-273, pred), new_pred_r, col = 'red', alpha=0.1, size=2)+ #adding curve density
    #geom_point(data=data, aes(x=Temp, y=Cells, color=Nutrients, shape=Predation),
     #          size = 2, position = position_dodge(width = 0.85), alpha=0.4)+ #plotting 
  #ploting SE
  theme_classic()+ # a more classic look
     theme(#panel.border = element_rect(colour = "black"),
       #legend.position ="none",
       legend.position =c(0.18, 0.7),
        #axis.text.x = element_text(size = 10), 
        axis.text.x = element_blank(), 
        axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
         axis.title.y = element_text(size = 12, hjust = 0.6, vjust = 2.5), 
         axis.text.y = element_text(size = 11), 
       #  legend.position ="none",
         strip.text = element_text(color = "black", face="bold", size = 15, hjust =0.2),
        # axis.line.x.top = element_blank(),
    #axis.line.y.right = element_blank(),
    strip.background = element_rect(fill = "white", color = "white"))+
  ylab("Population growth rate (r)")+
 xlab("Temperature (°C)")+
  scale_x_continuous(breaks = seq(14, 32, by = 2))+
  scale_colour_manual(values = c("High Nutrients"="#D55E00", "Low Nutrients"="#0072B2")) 

plot_r
```
## Cell density across nutrient and predation treatments and temperatures with TPC curves
```{r}
data$density<-data$Cells/3 # estimating density

sum_pred_density<-data %>% # calculating mean and standard error for plotting
  group_by(Temp, Nutrients, Predation) %>%
  summarise(mean=mean(density), sd=sd(density), #summarizing abundance 
            n=n()) %>% #summarizing richness
  mutate(se=sd/sqrt(n))

sum_pred_density #checking the summary 

pd <- position_dodge(width = 0.95)

plot_density<-ggplot() + #calling ggplot
  geom_point(data=sum_pred_density, aes(x=Temp, y=mean, color=Nutrients, shape=Predation, group = interaction(Nutrients, Predation)), 
             size = 2.5, position = pd)+
  geom_errorbar(data=sum_pred_density, aes(x=Temp, ymin=mean-se, ymax=mean+se, group = interaction(Nutrients, Predation), color=Nutrients),  
               size = 0.6, width = 0.2, alpha = 0.6, position = pd)+
  #  geom_point(data=data, aes(x=Temp, y=density, color=Nutrients, shape=Predation, group = interaction(Nutrients, Predation)),
          #     size = 1, position = pd, alpha=0.2)+ #plotting 
   geom_line(aes(T-273, pred), new_pred_density , col = 'red', alpha=0.1, size=2)+ #adding curve
  #ploting SE
  theme_classic()+ # a more classic look
     theme(#panel.border = element_rect(colour = "black"),
       axis.text.x = element_text(size = 10),
       axis.title.y = element_text(size = 12, hjust = 0.6, vjust = 2.5), 
       axis.text.y = element_text(size = 11), 
       legend.position = "none",
       #legend.position =c(0.10, 0.55),
        strip.text = element_text(color = "black", face="bold", size = 15, hjust =0.2),
        # axis.line.x.top = element_blank(),
    #axis.line.y.right = element_blank(),
    strip.background = element_rect(fill = "white", color = "white"))+
  ylab("Cell density (cells/ml)")+
  xlab("Temperature (°C)")+
    scale_x_continuous(breaks = seq(12, 34, by = 2))+
   scale_colour_manual(values = c("High Nutrients"="#D55E00", "Low Nutrients"="#0072B2"))

plot_density
```

### Figure 2 Effect treatments across temperatures 
```{r}
plot_r/plot_density
ggsave("figure/Density_r_TempTetra_.png", height = 25, width = 20, units = 'cm', dpi= 300, type = "cairo")
```


## Thermal performance curves across treatments
```{r}
# High Nutrients and No predation
data$T<-data$Temp+273

d<-data%>%
  filter(Nutrients=="High Nutrients" & Predation=="No predation ")

start_vals <- get_start_vals(d$T, d$r, model_name = 'sharpeschoolhigh_1981')

# Sharpe Schoolfield high model
fit_schoolfield_resp<-nls_multstart(r~sharpeschoolhigh_1981(temp = T, r_tref, e, eh, th, tref = 293),
data = d,
iter = c(3,3,3,3),
start_lower = start_vals - 10,
start_upper = start_vals + 10,
lower = get_lower_lims(d$T, d$r, model_name = 'sharpeschoolhigh_1981'),
upper = get_upper_lims(d$T, d$r, model_name = 'sharpeschoolhigh_1981'),
supp_errors = 'Y',
convergence_count = FALSE) 

# Creating predictions
newT <- data.frame(T = seq(min(d$T-5), max(d$T+5), length.out=100))
newT$pred <- predict(fit_schoolfield_resp, newdata = newT)
newTHn<-newT

#summary of model and calculation parameters 
summary(fit_schoolfield_resp)


params<-rTPC::calc_params(fit_schoolfield_resp)
toptHn<-params$topt
params

HnNpParams<-params

fit_schoolfield_resp_nlsLM<-minpack.lm::nlsLM(r~sharpeschoolhigh_1981(temp = T, r_tref, e, eh, th, tref = 293), 
          data=d,
          start = coef(fit_schoolfield_resp), #I just add the coeficient from my previously calculated model 
                        lower = get_lower_lims(d$T, d$r, model_name = 'sharpeschoolhigh_1981'),
                        upper = get_upper_lims(d$T, d$r, model_name = 'sharpeschoolhigh_1981'),
                        weights = rep(1, times = nrow(d)))

summary(fit_schoolfield_resp_nlsLM)

# bootstrap using case resampling
boot1 <- Boot(fit_schoolfield_resp_nlsLM, method = 'case')

#hist(boot1, layout = c(2,2))

boot1_preds <- boot1$t %>%
  as.data.frame() %>%
  drop_na() %>%
  mutate(iter = 1:n()) %>%
  group_by_all() %>%
  do(data.frame(T = seq(min(d$T-5), max(d$T+5), length.out = 100))) %>%
  ungroup() %>%
  mutate(pred = sharpeschoolhigh_1981(temp = T, r_tref, e, eh, th, tref = 293))

# calculate bootstrapped confidence intervals
boot1_conf_predsHn <- group_by(boot1_preds, T) %>%
  summarise(conf_lower = quantile(pred, 0.025),
            conf_upper = quantile(pred, 0.975)) %>%
  ungroup()

CI_Hn<-boot1_conf_predsHn

# Predation prediction with bootstraping interval confidences
ggplot() +
  geom_line(aes(T-273, pred), newTHn, col = 'blue') +
  geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper), boot1_conf_predsHn, fill = 'blue', alpha = 0.3) +
  geom_point(aes(T-273, r), d, size = 1, alpha = 0.5, position="jitter") +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       y = 'Respiration rates',
       title = 'Growth rate with low nutrients and no predation')+
  ylim(0, 9)

# Same for low nutrients and predation 
d<-data%>%
  filter(Nutrients=="Low Nutrients" & Predation=="No predation ")

start_vals <- get_start_vals(d$T, d$r, model_name = 'sharpeschoolhigh_1981')

# Sharpe Schoolfield full model
fit_schoolfield_resp<-nls_multstart(r~sharpeschoolhigh_1981(temp = T, r_tref, e, eh, th, tref = 293),
data = d,
iter = c(3,3,3,3),
start_lower = start_vals - 10,
start_upper = start_vals + 10,
lower = get_lower_lims(d$T, d$r, model_name = 'sharpeschoolhigh_1981'),
upper = get_upper_lims(d$T, d$r, model_name = 'sharpeschoolhigh_1981'),
supp_errors = 'Y',
convergence_count = FALSE) 

# Creating predictions
newT <- data.frame(T = seq(min(d$T-5), max(d$T+5), length.out=100))
newT$pred <- predict(fit_schoolfield_resp, newdata = newT)
newTLn<-newT

#summary of model and calculation parameters 
summary(fit_schoolfield_resp)

params<-rTPC::calc_params(fit_schoolfield_resp)
toptLn<-params$topt
params

LnNpParams<-params

fit_schoolfield_resp_nlsLM<-minpack.lm::nlsLM(r~sharpeschoolhigh_1981(temp = T, r_tref, e, eh, th, tref = 293), 
          data=d,
          start = coef(fit_schoolfield_resp), #I just add the coeficient from my previously calculated model 
                        lower = get_lower_lims(d$T, d$r, model_name = 'sharpeschoolhigh_1981'),
                        upper = get_upper_lims(d$T, d$r, model_name = 'sharpeschoolhigh_1981'),
                        weights = rep(1, times = nrow(d)))

summary(fit_schoolfield_resp_nlsLM)

# Bootstraping for confidence interval
boot1 <- Boot(fit_schoolfield_resp_nlsLM, method = 'case')

#hist(boot1, layout = c(2,2))

boot1_preds <- boot1$t %>%
  as.data.frame() %>%
  drop_na() %>%
  mutate(iter = 1:n()) %>%
  group_by_all() %>%
  do(data.frame(T = seq(min(d$T-5), max(d$T+5), length.out = 100))) %>%
  ungroup() %>%
  mutate(pred =sharpeschoolhigh_1981(temp = T, r_tref, e, eh, th, tref = 293))


# calculate bootstrapped confidence intervals
boot1_conf_predsLn <- group_by(boot1_preds, T) %>%
  summarise(conf_lower = quantile(pred, 0.025),
            conf_upper = quantile(pred, 0.975)) %>%
  ungroup()

CI_Ln<-boot1_conf_predsLn

# Predation prediction with bootstraping interval confidences
ggplot() +
  geom_line(aes(T-273, pred), newTLn, col = 'blue') +
  geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper), boot1_conf_predsLn, fill = 'blue', alpha = 0.3) +
  geom_point(aes(T-273, r), d, size = 1, alpha = 0.5, position="jitter") +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       y = 'Respiration rates',
       title = 'Growth rate with low nutrients and no predation')+
  ylim(0, 9)


# For high nutrients and predation 
d<-data%>%
  filter(Nutrients=="High Nutrients" & Predation=="Predation present ")


start_vals <- get_start_vals(d$T, d$r, model_name = 'sharpeschoolhigh_1981')

# Sharpe Schoolfield full model
fit_schoolfield_resp<-nls_multstart(r~sharpeschoolhigh_1981(temp = T, r_tref, e, eh, th, tref = 293),
data = d,
iter = c(3,3,3,3),
start_lower = start_vals - 10,
start_upper = start_vals + 10,
lower = get_lower_lims(d$T, d$r, model_name = 'sharpeschoolhigh_1981'),
upper = get_upper_lims(d$T, d$r, model_name = 'sharpeschoolhigh_1981'),
supp_errors = 'Y',
convergence_count = FALSE) 

# Creating predictions
newT <- data.frame(T = seq(min(d$T-5), max(d$T+5), length.out=100))
newT$pred <- predict(fit_schoolfield_resp, newdata = newT)
newTHnPp<-newT

#summary of model and calculation parameters 
summary(fit_schoolfield_resp)

params<-rTPC::calc_params(fit_schoolfield_resp)
toptHnPp<-params$topt
params

HnYpParams<-params

fit_schoolfield_resp_nlsLM<-minpack.lm::nlsLM(r~sharpeschoolhigh_1981(temp = T, r_tref, e, eh, th, tref = 293), 
          data=d,
          start = coef(fit_schoolfield_resp), #I just add the coeficient from my previously calculated model 
                        lower = get_lower_lims(d$T, d$r, model_name = 'sharpeschoolhigh_1981'),
                        upper = get_upper_lims(d$T, d$r, model_name = 'sharpeschoolhigh_1981'),
                        weights = rep(1, times = nrow(d)))

summary(fit_schoolfield_resp_nlsLM)

# bootstrap using case resampling
boot1 <- Boot(fit_schoolfield_resp_nlsLM, method = 'case')

#hist(boot1, layout = c(2,2))

boot1_preds <- boot1$t %>%
  as.data.frame() %>%
  drop_na() %>%
  mutate(iter = 1:n()) %>%
  group_by_all() %>%
  do(data.frame(T = seq(min(d$T-5), max(d$T+5), length.out = 100))) %>%
  ungroup() %>%
  mutate(pred = sharpeschoolhigh_1981(temp = T, r_tref, e, eh, th, tref = 293))

# calculate bootstrapped confidence intervals
boot1_conf_predsHnPp <- group_by(boot1_preds, T) %>%
  summarise(conf_lower = quantile(pred, 0.025),
            conf_upper = quantile(pred, 0.975)) %>%
  ungroup()

CI_HnPp<-boot1_conf_predsHnPp

# Predation prediction with bootstraping interval confidences
ggplot() +
  geom_line(aes(T-273, pred), newTHnPp, col = 'blue') +
  geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper), boot1_conf_predsHnPp, fill = 'blue', alpha = 0.3) +
  geom_point(aes(T-273, r), d, size = 1, alpha = 0.5, position="jitter") +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       y = 'Respiration rates',
       title = 'Growth rate with high nutrients and predation')+
  ylim(0, 9)

# same for low nutrients and predation 
d<-data%>%
  filter(Nutrients=="Low Nutrients" & Predation=="Predation present ")

start_vals <- get_start_vals(d$T, d$r, model_name = 'sharpeschoolhigh_1981')

# Sharpe Schoolfield full model
fit_schoolfield_resp<-nls_multstart(r~sharpeschoolhigh_1981(temp = T, r_tref, e, eh, th, tref = 293),
data = d,
iter = c(3,3,3,3),
start_lower = start_vals - 10,
start_upper = start_vals + 10,
lower = get_lower_lims(d$T, d$r, model_name = 'sharpeschoolhigh_1981'),
upper = get_upper_lims(d$T, d$r, model_name = 'sharpeschoolhigh_1981'),
supp_errors = 'Y',
convergence_count = FALSE) 

# Creating predictions
newT <- data.frame(T = seq(min(d$T-5), max(d$T+5), length.out=100))
newT$pred <- predict(fit_schoolfield_resp, newdata = newT)
newTLnPp<-newT

#summary of model and calculation parameters 
summary(fit_schoolfield_resp)

params<-rTPC::calc_params(fit_schoolfield_resp)
toptLnPp<-params$topt
params

LnYPparams<-params

fit_schoolfield_resp_nlsLM<-minpack.lm::nlsLM(r~sharpeschoolhigh_1981(temp = T, r_tref, e, eh, th, tref = 293), 
          data=d,
          start = coef(fit_schoolfield_resp), #I just add the coeficient from my previously calculated model 
                        lower = get_lower_lims(d$T, d$r, model_name = 'sharpeschoolhigh_1981'),
                        upper = get_upper_lims(d$T, d$r, model_name = 'sharpeschoolhigh_1981'),
                        weights = rep(1, times = nrow(d)))

summary(fit_schoolfield_resp_nlsLM)

# bootstrap using case resampling
boot1 <- Boot(fit_schoolfield_resp_nlsLM, method = 'case')

#hist(boot1, layout = c(2,2))

boot1_preds <- boot1$t %>%
  as.data.frame() %>%
  drop_na() %>%
  mutate(iter = 1:n()) %>%
  group_by_all() %>%
  do(data.frame(T = seq(min(d$T-5), max(d$T+5), length.out = 100))) %>%
  ungroup() %>%
  mutate(pred = sharpeschoolhigh_1981(temp = T, r_tref, e, eh, th, tref = 293))

# calculate bootstrapped confidence intervals
boot1_conf_predsLnPp <- group_by(boot1_preds, T) %>%
  summarise(conf_lower = quantile(pred, 0.025),
            conf_upper = quantile(pred, 0.975)) %>%
  ungroup()

CI_LnPp<-boot1_conf_predsLnPp

# Predation prediction with bootstraping interval confidences
ggplot() +
  geom_line(aes(T-273, pred), newTLnPp, col = 'blue') +
  geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper), boot1_conf_predsLn, fill = 'blue', alpha = 0.3) +
  geom_point(aes(T-273, r), d, size = 1, alpha = 0.5, position="jitter") +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       y = 'Respiration rates',
       title = 'Growth rate with low nutrients and predation present')+
  ylim(0, 9)

```
### Figure 1: TPCs across treatments 
```{r}
d<-data

tpc2<-ggplot() +
  geom_line(aes(T-273, pred), newTHn, col = '#00A087FF', size=0.7) +
  geom_line(aes(T-273, pred), newTLn, col = '#F39B7FB2', size=0.7) +
  geom_line(aes(T-273, pred), newTHnPp, col = 'darkgreen', size=0.7) +
  geom_line(aes(T-273, pred), newTLnPp, col = 'lightsalmon4', size=0.7) +
  geom_point(aes(Temp, r, color=Cat), d, size = 1.5, alpha = 0.5)+ 
  #position="jitter"        
  geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper), CI_Hn, fill = '#00A087FF', alpha = 0.2) +
  geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper),CI_Ln, fill = '#F39B7FB2', alpha = 0.2) +
  geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper), CI_HnPp, fill = 'darkgreen', alpha = 0.2) +
  geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper),CI_LnPp, fill = 'lightsalmon4', alpha = 0.2) +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       y = 'Growth rate (r)')+
  scale_y_continuous(limits=c(-0.06, 8))+
scale_x_continuous(limits=c(9, 38), breaks=seq(10, 38, 2))+
  theme(legend.position = c(0.19, 0.75),
         legend.key.spacing.y = unit(0.3, "cm"),
         legend.text = element_text(size = 10.5),
         panel.grid.major = element_blank(), 
         panel.grid.minor = element_blank(), 
         panel.background = element_rect(colour="white"), 
         panel.border = element_blank(),
         axis.line = element_line(colour = "black"),
         #axis.line.x.top = element_line(colour="black"),
         #axis.line.y.right = element_line(colour="black"),
         #axis.line.y.left = element_line(colour="black"),
         strip.background=element_rect(colour="white", fill="white"),
         strip.text = element_text(face = "italic", 
                                   color = "black", size = 13, hjust =0.05))+
          scale_colour_manual(name = "", 
 values =c('High NutrientsNo'="#00A087FF", 'High NutrientsYes'="darkgreen", 'Low NutrientsNo'="#F39B7FB2", 'Low NutrientsYes'="lightsalmon4"), 
 labels= c('High NutrientsNo'="High Nutrients/No predation", 'Low NutrientsNo'="Low Nutrients/No predation", 'High NutrientsYes'="High Nutrients/Predation present", 'Low NutrientsYes'="Low Nutrients/Predation present"))
# +
#   geom_vline(xintercept=toptHn-273, linetype="dashed", size=0.5, color="#00A087FF")+
#   geom_vline(xintercept=toptLn-273, linetype="dashed", size=0.5, color="#F39B7FB2")+
#   geom_vline(xintercept=toptHnPp-273, linetype="dashed", size=0.5, color="darkgreen")+
#   geom_vline(xintercept=toptLnPp-273, linetype="dashed", size=0.5, color="lightsalmon4")

tpc2

ggsave("figure/TPC_Schoolfield_final.png", height = 13, width = 20, units = 'cm', dpi= 300, type = "cairo")
```

### Estimation of thermal parameters
```{r}
d<-data

# fitting a  model
start_vals <- get_start_vals(d$T, d$r, "sharpeschoolhigh_1981")
lower      <- get_lower_lims(d$T, d$r, "sharpeschoolhigh_1981")
upper      <- get_upper_lims(d$T, d$r, "sharpeschoolhigh_1981")

#Function for fitting SchoolfieldHigh model
fit_schoolfied_replica <- function(d) {
  
  if (nrow(d) < 6) return(NULL)
  
  tryCatch(
    nls_multstart(
      r ~ sharpeschoolhigh_1981(
       temp = T, 
       r_tref, 
       e, 
       eh, 
       th, 
       tref = 293),
      data = d,
    iter = c(5, 5, 5, 5),
    start_lower = get_start_vals(d$T, d$r, "sharpeschoolhigh_1981") - 2,
    start_upper = get_start_vals(d$T, d$r, "sharpeschoolhigh_1981") + 2,
    lower = get_lower_lims(d$T, d$r, "sharpeschoolhigh_1981"),
    upper = get_upper_lims(d$T, d$r, "sharpeschoolhigh_1981"),
    supp_errors = "Y",
    convergence_count = FALSE
    ),
    error = function(e) NULL
  )
}

#Fitting model into our data
fits_rep <- d %>%
  group_by(Cat, Rep) %>%
  group_modify(~{
    tibble(
      schoolfield = list(fit_schoolfied_replica(.x))
    )
  }) %>%
  ungroup()

#Creating a function for extracting all paramters
extract_all_params <- function(mod) {

  if (is.null(mod)) return(NULL)

  # safe wrappers
  safe_topt <- purrr::possibly(get_topt, otherwise = NA_real_)
  safe_rmax <- purrr::possibly(get_rmax, otherwise = NA_real_)
  safe_q10  <- purrr::possibly(function(mod) {
    # Q10 manual
    safe_q10_manual <- function(mod, t1 = 283, t2 = 293) {
      r1 <- try(predict(mod, newdata = data.frame(T = t1)), silent = TRUE)
      r2 <- try(predict(mod, newdata = data.frame(T = t2)), silent = TRUE)
      if (inherits(r1, "try-error") || inherits(r2, "try-error")) return(NA_real_)
      if (is.na(r1) || is.na(r2) || r1 <= 0 || r2 <= 0) return(NA_real_)
      (r2 / r1)^(10 / (t2 - t1))
    }
    
    safe_q10_manual(mod)
  }, otherwise = NA_real_)
  
  # Coefficients
  coefs <- coef(mod)

  # Derived parameters
  Pmax <- safe_rmax(mod)
  Topt <- safe_topt(mod)
  Q10  <- safe_q10(mod)

  # CTmin and CTmax at 5% of Pmax
  safe_ct <- purrr::possibly(function(mod, frac = 0.2) {
    temps <- seq(min(mod$model$T) - 10, max(mod$model$T) + 10, length.out = 2000)
    preds <- predict(mod, newdata = data.frame(T = temps))
    # remove negative predictions
    preds[preds < 0] <- 0
    # find first temp >= frac*Pmax (CTmin)
    CTmin <- temps[min(which(preds >= frac*Pmax))]
    # find last temp >= frac*Pmax (CTmax)
    CTmax <- temps[max(which(preds >= frac*Pmax))]
    tibble(CTmin = CTmin, CTmax = CTmax)
  },
  otherwise = tibble(CTmin = NA_real_, CTmax = NA_real_))

  CTs <- safe_ct(mod)
  
# Thermal breadth at 80% of Pmax
  
safe_breadth80 <- purrr::possibly(function(mod, level = 0.8) {
  
  temps <- seq(min(mod$model$T) - 10,
               max(mod$model$T) + 10,
               length.out = 2000)
  
  preds <- predict(mod, newdata = data.frame(T = temps))

# clean predictions
  preds[!is.finite(preds)] <- NA
  preds[preds < 0] <- 0
  
  Pmax_pred <- max(preds, na.rm = TRUE)
  
  if (!is.finite(Pmax_pred) || Pmax_pred <= 0) {
    return(NA_real_)
  }
  
  idx <- which(preds >= level * Pmax_pred)
  
  if (length(idx) <= 1) {
    return(NA_real_)
  }
  
  temps[max(idx)] - temps[min(idx)]
  
}, otherwise = NA_real_)

Breadth80 <- safe_breadth80(mod)

  tibble(
    r_tref = coefs[["r_tref"]],
    E      = coefs[["e"]],
    Eh     = coefs[["eh"]],
    Th     = coefs[["th"]],
    Topt   = Topt,
    Pmax   = Pmax,
    Q10    = Q10,
    CTmin  = CTs$CTmin,
    CTmax  = CTs$CTmax,
    Breadth80 = Breadth80
  )
}


# Fitting our data to the function to get parameters
params_individual <- fits_rep %>%
   mutate(params = purrr::map(schoolfield, extract_all_params)) %>%
   tidyr::unnest(params)


## Sumarizing parameters mean and se for plots
 se <- function(x) {
   sd(x, na.rm = TRUE) / sqrt(sum(!is.na(x)))
 }

params_summary <- params_individual %>%
  group_by(Cat) %>%   # or any grouping variable
  summarise(
    r_tref_mean = mean(r_tref, na.rm = TRUE),
    r_tref_se   = se(r_tref),

    E_mean      = mean(E, na.rm = TRUE),
    E_se        = se(E),

    Eh_mean     = mean(Eh, na.rm = TRUE),
    Eh_se       = se(Eh),

    Th_mean     = mean(Th, na.rm = TRUE),
    Th_se       = se(Th),

    Topt_mean   = mean(Topt, na.rm = TRUE),
    Topt_se     = se(Topt),

    Pmax_mean   = mean(Pmax, na.rm = TRUE),
    Pmax_se     = se(Pmax),

    Q10_mean    = mean(Q10, na.rm = TRUE),
    Q10_se      = se(Q10),

  n=n(),

  ) %>%
  ungroup()

params_summary<-params_summary%>%
  mutate(Topt_mean=Topt_mean-273)

params_summary
```
### Plotting rmax and topt 
```{r}
params_long <- params_summary %>%
  pivot_longer(
    cols = -c(Cat, n),        # keep Species and n
    names_to = "name",
    values_to = "value"
  ) %>%
  # separate mean and se
  mutate(
    stat = ifelse(grepl("_mean$", name), "mean",
                  ifelse(grepl("_se$", name), "se", NA)),
    parameter = sub("(_mean|_se)$", "", name)
  ) %>%
  select(Cat, n, parameter, stat, value) %>%
  pivot_wider(
    names_from = stat,
    values_from = value
  )

## Plotting Pmax
params_summary_plot<-params_long %>%
   filter(parameter %in% c("Pmax"))


params_individual_filt<-params_individual %>%
  select(Cat, Pmax)%>%
   #mutate(Topt=Topt-273)%>%
  pivot_longer(
    cols = -c(Cat),        # keep Species and n
    names_to = "name",
    values_to = "value")

new_names <- c("Pmax" = "Maximum growth rate (r)")

param_plot_pmax<-
  ggplot()+
  geom_point(data =params_individual_filt, aes(x = Cat, y = value, color=Cat), position = position_dodge(width = 0.85))+ 
       #    shape = 1, alpha = 0.4,  
      #    position = position_jitterdodge(jitter.width = NULL, jitter.height =0.01, dodge.width = 0.85)) +
 # this plots SE behind the mean, can use also CI with summarize
  geom_point(data = params_summary_plot, aes(x=Cat, y = mean, colour = Cat), 
              shape = "-", size = 20, position = position_dodge(width = 0.85)) +
    geom_errorbar(data = params_summary_plot, aes(x=Cat, ymin = mean-se, ymax = mean+se, colour = Cat), 
                size = 8, width = 0, alpha = 0.3, position = position_dodge(width = 0.85), 
                show.legend = FALSE) +
  # plots the mean value 
  theme_bw()+
   theme(axis.text.x = element_blank(),
#        axis.title.y = element_text(size = 10.5, hjust = 0.6, vjust = 2.5),
        axis.title.y = element_blank(),
        axis.ticks = element_blank(),
        legend.position="none",
        #legend.position = c(0.08, 0.85),
         legend.key.spacing.y = unit(-0.9, "cm"),
       # legend.key.height = unit(0.1, "cm"),
       # legend.spacing.y = unit(1, 'cm'),
          legend.key.size = unit(-1, "cm"),
        legend.margin = margin(0, 0, 0, 0),
         legend.text = element_text(margin = margin(l = -15, unit = "pt"), size = 8),
        legend.title = element_blank())+
#  #  guides(fill = guide_legend(byrow = TRUE))+
     #legend.text = element_text(margin = margin(l = -5, unit = "pt"))+
#    scale_colour_manual(name = "", values = c(M.peninsularisB="#F39B7FB2", H.princeps="#00A087FF"), labels = c(expression(italic("M.peninsularis")), expression(italic("H.princeps")))) +
#   #ylab(expression(italic("E/Eh")))+
   xlab("")+
  # ylab()
   facet_wrap(~parameter, scales = "free_y", labeller = as_labeller(new_names))+
scale_colour_manual(name = "", 
 values =c('High NutrientsNo'="#00A087FF", 'High NutrientsYes'="darkgreen", 'Low NutrientsNo'="#F39B7FB2", 'Low NutrientsYes'="lightsalmon4"), 
 labels= c('High NutrientsNo'="High Nutrients/No predation", 'Low NutrientsNo'="Low Nutrients/No predation", 'High NutrientsYes'="High Nutrients/Predation", 'Low NutrientsYes'="Low Nutrients/Predation"))

param_plot_pmax


## for topt
params_summary_plot<-params_long %>%
   filter(parameter %in% c("Topt"))


params_individual_filt<-params_individual %>%
  select(Cat, Topt)%>%
   mutate(Topt=Topt-273)%>%
  pivot_longer(
    cols = -c(Cat),        # keep Species and n
    names_to = "name",
    values_to = "value")

# %>%
#    pivot_wider(
#     names_from = stat,
#     values_from = value
#   )
 
#Changing name to title
new_names <- c("Topt" = "Thermal optimum (°C)")

param_plot_topt<-
  ggplot()+
  geom_point(data =params_individual_filt, aes(x = Cat, y = value, color=Cat), position = position_dodge(width = 0.85))+ 
       #    shape = 1, alpha = 0.4,  
      #    position = position_jitterdodge(jitter.width = NULL, jitter.height =0.01, dodge.width = 0.85)) +
 # this plots SE behind the mean, can use also CI with summarize
  geom_point(data = params_summary_plot, aes(x =Cat, y = mean, colour = Cat), 
              shape = "-", size = 20, position = position_dodge(width = 0.85)) +
    geom_errorbar(data = params_summary_plot, aes(x = Cat, ymin = mean-se, ymax = mean+se, colour = Cat), 
                size = 8, width = 0, alpha = 0.3, position = position_dodge(width = 0.85), 
                show.legend = FALSE) +
  # plots the mean value 
  theme_bw()+
   theme(axis.text.x = element_blank(),
#        axis.title.y = element_text(size = 10.5, hjust = 0.6, vjust = 2.5),
        axis.title.y = element_blank(),
        axis.ticks = element_blank(),
        legend.position="none",
        #legend.position = c(0.08, 0.85),
         legend.key.spacing.y = unit(-0.9, "cm"),
       # legend.key.height = unit(0.1, "cm"),
       # legend.spacing.y = unit(1, 'cm'),
          legend.key.size = unit(-1, "cm"),
        legend.margin = margin(0, 0, 0, 0),
         legend.text = element_text(margin = margin(l = -15, unit = "pt"), size = 8),
        legend.title = element_blank())+
#  #  guides(fill = guide_legend(byrow = TRUE))+
     #legend.text = element_text(margin = margin(l = -5, unit = "pt"))+
#    scale_colour_manual(name = "", values = c(M.peninsularisB="#F39B7FB2", H.princeps="#00A087FF"), labels = c(expression(italic("M.peninsularis")), expression(italic("H.princeps")))) +
#   #ylab(expression(italic("E/Eh")))+
   xlab("")+
   facet_wrap(~parameter, scales = "free_y", labeller = as_labeller(new_names))+
scale_colour_manual(name = "", 
 values =c('High NutrientsNo'="#00A087FF", 'High NutrientsYes'="darkgreen", 'Low NutrientsNo'="#F39B7FB2", 'Low NutrientsYes'="lightsalmon4"), 
 labels= c('High NutrientsNo'="High Nutrients/No predation", 'Low NutrientsNo'="Low Nutrients/No predation", 'High NutrientsYes'="High Nutrients/Predation", 'Low NutrientsYes'="Low Nutrients/Predation"))
#+
  # Add a single letter 'A' at coordinates x=3, y=30
 # annotate("A", x = 3, y = 30, label = "A", size = 8, #fontface = "bold")
  
param_plot_topt
```
Testing for statistically significant differences
```{r}
mod_Topt<-lm(Topt~Cat, data=params_individual)
summary(mod_Topt)
pairs(emmeans (mod_Topt,  ~ Cat, adjust = "none"))

mod_Pmax<-lm(Pmax~Cat, data=params_individual)
summary(mod_Pmax)

pairs(emmeans (mod_Pmax,  ~ Cat, adjust = "none"))
```

### Calcuating performance above 20%
```{r}

# High nutrients and no predation
data$K<-data$T
d<-data %>%
  filter(Cat=="High NutrientsNo")



PmaxHnNp<-params_summary%>%
  select(Cat, Pmax_mean)%>%
  filter(Cat=="High NutrientsNo")

Pmax75_HnNp<-0.2*PmaxHnNp$Pmax_mean

# fitting a  model
start_vals <- get_start_vals(d$K, d$r, "sharpeschoolhigh_1981")
lower      <- get_lower_lims(d$K, d$r, "sharpeschoolhigh_1981")
upper      <- get_upper_lims(d$K, d$r, "sharpeschoolhigh_1981")


# fitting a schoolfield model
fit_schoolfield_resp<- nls_multstart(r~sharpeschoolhigh_1981(temp = K, r_tref, e, eh, th, tref = 293),
data = d,
iter = c(3, 3, 3, 3),
start_lower = start_vals - 10,
start_upper = start_vals + 10,
lower = get_lower_lims(d$K, d$r, model_name = 'sharpeschoolhigh_1981'),
upper = get_upper_lims(d$K, d$r, model_name = 'sharpeschoolhigh_1981'),
supp_errors = 'Y',
convergence_count = FALSE)

# Creating predictions
newT <- data.frame(K = seq(min(d$K-5), max(d$K+5), length.out=100))
newT$pred <- predict(fit_schoolfield_resp, newdata = newT)

newTHnNp<-newT

newTHnNp_75<-newTHnNp %>%
  filter(pred>Pmax75_HnNp)

Temp_HnNp_75<-data.frame((min(newTHnNp_75$K)-273), (max(newTHnNp_75$K)-273))
Temp_HnNp_75

# High nutrients and predation
d<-data%>%
  filter(Cat=="High NutrientsYes")

PmaxHnYp<-params_summary%>%
  select(Cat, Pmax_mean)%>%
  filter(Cat=="High NutrientsYes")

Pmax75_HnYp<-0.2*PmaxHnYp$Pmax_mean

# fitting a  model
start_vals <- get_start_vals(d$K, d$r, "sharpeschoolhigh_1981")
lower      <- get_lower_lims(d$K, d$r, "sharpeschoolhigh_1981")
upper      <- get_upper_lims(d$K, d$r, "sharpeschoolhigh_1981")


# fitting a schoolfield model
fit_schoolfield_resp<- nls_multstart(r~sharpeschoolhigh_1981(temp = K, r_tref, e, eh, th, tref = 293),
data = d,
iter = c(3, 3, 3, 3),
start_lower = start_vals - 10,
start_upper = start_vals + 10,
lower = get_lower_lims(d$K, d$r, model_name = 'sharpeschoolhigh_1981'),
upper = get_upper_lims(d$K, d$r, model_name = 'sharpeschoolhigh_1981'),
supp_errors = 'Y',
convergence_count = FALSE)

# Creating predictions
newT <- data.frame(K = seq(min(d$K-5), max(d$K+5), length.out=100))
newT$pred <- predict(fit_schoolfield_resp, newdata = newT)

newTHnYp<-newT

newTHnYp_75<-newTHnYp %>%
  filter(pred>Pmax75_HnYp)

Temp_HnYp_75<-data.frame((min(newTHnYp_75$K)-273), (max(newTHnYp_75$K)-273))
Temp_HnYp_75

## Low nutrients and no predation
d<-data%>%
  filter(Cat=="Low NutrientsNo")

PmaxLnNp<-params_summary%>%
  select(Cat, Pmax_mean)%>%
  filter(Cat=="Low NutrientsNo")

Pmax75LnNp<-0.2*PmaxLnNp$Pmax_mean

# fitting a  model
start_vals <- get_start_vals(d$K, d$r, "sharpeschoolhigh_1981")
lower      <- get_lower_lims(d$K, d$r, "sharpeschoolhigh_1981")
upper      <- get_upper_lims(d$K, d$r, "sharpeschoolhigh_1981")


# fitting a schoolfield model
fit_schoolfield_resp<- nls_multstart(r~sharpeschoolhigh_1981(temp = K, r_tref, e, eh, th, tref = 293),
data = d,
iter = c(3, 3, 3, 3),
start_lower = start_vals - 10,
start_upper = start_vals + 10,
lower = get_lower_lims(d$K, d$r, model_name = 'sharpeschoolhigh_1981'),
upper = get_upper_lims(d$K, d$r, model_name = 'sharpeschoolhigh_1981'),
supp_errors = 'Y',
convergence_count = FALSE)


# Creating predictions
newT <- data.frame(K = seq(min(d$K-2), max(d$K+2), length.out=100))
newT$pred <- predict(fit_schoolfield_resp, newdata = newT)

newTLnNp<-newT

newTLnNp_75<-newTLnNp %>%
  filter(pred>Pmax75LnNp)

Temp_LnNp_75<-data.frame((min(newTLnNp_75$K)-273), (max(newTLnNp_75$K)-273))
Temp_LnNp_75

#Low nutrients and predation
d<-data%>%
  filter(Cat=="Low NutrientsYes")

PmaxLnYp<-params_summary%>%
  select(Cat, Pmax_mean)%>%
  filter(Cat=="Low NutrientsYes")

Pmax75_LnYp<-0.2*PmaxLnYp$Pmax_mean

# fitting a  model
start_vals <- get_start_vals(d$K, d$r, "sharpeschoolhigh_1981")
lower      <- get_lower_lims(d$K, d$r, "sharpeschoolhigh_1981")
upper      <- get_upper_lims(d$K, d$r, "sharpeschoolhigh_1981")


# fitting a schoolfield model
fit_schoolfield_resp<- nls_multstart(r~sharpeschoolhigh_1981(temp = K, r_tref, e, eh, th, tref = 293),
data = d,
iter = c(5, 5, 5, 5),
start_lower = start_vals - 10,
start_upper = start_vals + 10,
lower = get_lower_lims(d$K, d$r, model_name = 'sharpeschoolhigh_1981'),
upper = get_upper_lims(d$K, d$r, model_name = 'sharpeschoolhigh_1981'),
supp_errors = 'Y',
convergence_count = FALSE)


# Creating predictions
newT <- data.frame(K = seq(min(d$K-2), max(d$K+2), length.out=100))
newT$pred <- predict(fit_schoolfield_resp, newdata = newT)

newTLnYp<-newT

newTLnYp_75<-newTLnYp %>%
  filter(pred>Pmax75_LnYp)

Temp_LnYp_75<-data.frame((min(newTLnYp_75$K)-273), (max(newTLnYp_75$K)-273))

Temp_LnYp_75

## creating the data frame
minHnNp<-Temp_HnNp_75$X.min.newTHnNp_75.K....273.
maxHnNp<-Temp_HnNp_75$X.max.newTHnNp_75.K....273.

minHnYp<-Temp_HnYp_75$X.min.newTHnYp_75.K....273.
maxHnYp<-Temp_HnYp_75$X.max.newTHnYp_75.K....273.

minLnNp<-Temp_LnNp_75$X.min.newTLnNp_75.K....273.
maxLnNp<-Temp_LnNp_75$X.max.newTLnNp_75.K....273.

minLnYp<-Temp_LnYp_75$X.min.newTLnYp_75.K....273.
maxLnYp<-Temp_LnYp_75$X.max.newTLnYp_75.K....273.


df<-data.frame(
  Treatment=c("High Nutrients/No Predation", "High Nutrients/Predation", "Low Nutrients/No Predation", "Low Nutrients/Predation"),
  MinT=c(minHnNp, minHnYp, minLnNp, minLnYp),
  MaxT=c(maxHnNp, maxHnYp, maxLnNp, maxLnYp)
)

df<-df%>%
  mutate(Tbread=MaxT-MinT)
```

ploting
```{r}
df$Panel <- paste("Thermal breadth (","\u00B0C",")")

t_breadth_2<-
ggplot() +
  geom_errorbar(
    data = df,
    aes(x = fct_rev(Treatment), ymin = MinT, ymax = MaxT, color = Treatment),
    size = 2, width = 0.4, alpha = 0.3,
    position = position_dodge(width = 0.85),
    show.legend = FALSE
  ) +
  facet_wrap(~ Panel) +
  theme_bw() +
  theme(
    strip.background = element_rect(fill = "#D3D3D3", colour = "black"),
    strip.text = element_text(color = "black"),
    axis.text.x = element_blank(),
    axis.title.x = element_blank(),
    axis.ticks = element_blank()
  ) +
  ylab("") +
  scale_y_continuous(limits = c(14, 34), breaks = seq(14, 34, 2)) +
  scale_colour_manual(values = c(
    'High Nutrients/No Predation' = "#00A087FF",
    'High Nutrients/Predation' = "darkgreen",
    'Low Nutrients/No Predation' = "#F39B7FB2",
    'Low Nutrients/Predation' = "lightsalmon4"
  ))

t_breadth_2
```

#### Figure Thermal parameters
```{r}
# Grouping T breadth and pmax and topt
TPC_Tparam2<-(param_plot_topt|param_plot_pmax|t_breadth_2) +
  plot_layout(heights = c(1,1, 0.6), width=c(0.8, 0.8, 1.2)) &
  theme(panel.grid = element_blank())

Fig_1b_1<-(tpc2)/(TPC_Tparam2)+
   plot_layout(heights = c(1, 0.8), width=c(1,1))
 
Fig_1b_1

ggsave("figure/TPC_Parameters.png", height = 22, width = 20, units = 'cm', dpi= 300, type = "cairo")
```

