---
title: "FoodPredatTPCs"
output: html_document
date: "2026-01-20"
---

# Effect predation and nutrient limitation in Tetra TP

libraries
```{r}
library(tidyr)
library(dplyr)
library(ggplot2)
library(lme4)
library(emmeans)
library(rTPC)
library(nls.multstart)
library(boot)
library(car)
library(broom)
library(purrr)

```

Loading data
```{r}
data<-read.csv(file="exp1.csv", header=TRUE)
str(data)

#data$Temp<-factor(data$Temp)
```

summarizing data
```{r}
sum_pred<-data %>%
  group_by(Temp, Nutrients, Predation) %>%
  summarise(mean=mean(Cells), sd=sd(Cells), #summarizing abundance 
            n=n()) %>% #summarizing richness
  mutate(se=sd/sqrt(n))

sum_pred
```

```{r}

pd <- position_dodge(width = 0.95)

ggplot() + #calling ggplot
  geom_point(data=sum_pred, aes(x=Temp, y=mean, color=Nutrients, shape=Predation, group = interaction(Nutrients, Predation)), 
             size = 2.5, position = pd)+
  geom_errorbar(data=sum_pred, aes(x=Temp, ymin=mean-se, ymax=mean+se, group = interaction(Nutrients, Predation), color=Nutrients),  
               size = 0.6, width = 0.2, alpha = 0.6, position = pd)+
    geom_point(data=data, aes(x=Temp, y=Cells, color=Nutrients, shape=Predation, group = interaction(Nutrients, Predation)),
               size = 1, position = pd, alpha=0.2)+ #plotting 
  #ploting SE
  theme_classic()+ # a more classic look
     theme(#panel.border = element_rect(colour = "black"),
         axis.text.x = element_text(size = 10                       #margin = margins(t = 10, b = 5)
                                    ), 
        # axis.title.x = element_blank(), 
         axis.title.y = element_text(size = 12, hjust = 0.6, vjust = 2.5), 
         axis.text.y = element_text(size = 11), 
        legend.position =c(0.10, 0.35),
         strip.text = element_text(color = "black", face="bold", size = 15, hjust =0.2),
        # axis.line.x.top = element_blank(),
    #axis.line.y.right = element_blank(),
    strip.background = element_rect(fill = "white", color = "white"))+
  ylab("Number of cells")+
  xlab("Temperature (°C)")+
    scale_x_continuous(breaks = seq(12, 34, by = 2))+
   scale_colour_manual(values = c("High Nutrients"="#D55E00", "Low Nutrients"="#0072B2")) 


ggsave("NutPredTPC_Tetra.png", height = 13, width = 20, units = 'cm', dpi= 300, type = "cairo")
```
Modelling the effect of the factors
```{r}
str(data)

data$Nutrients<-(factor(data$Nutrients))
data$Predation<-(factor(data$Predation))

data$group <- interaction(data$Nutrients, data$Predation, drop = TRUE)
# levels will look like: "low.no", "high.no", "low.yes", "high.yes"

# --- Model: group-specific smooths of temperature + group intercepts
library(mgcv)
m_gam <- gam(
  Cells ~ group + s(Temp, by = group, k = 6, bs = "cr"),
  method = "REML",
  data = data
)

summary(m_gam)
gam.check(m_gam)

## Turning it into a table

param <- as.data.frame(summary(m_gam)$p.table)

param$Term <- rownames(param)

# this is the parametric table
param_pub <- param %>%
  dplyr::mutate(
    `Estimate ± SE` = paste0(round(Estimate, 2), " ± ", round(`Std. Error`, 2)),
    t = round(`t value`, 2),
    p = ifelse(`Pr(>|t|)` < 0.001, "<0.001", round(`Pr(>|t|)`, 3))
  ) %>%
  dplyr::select(Term, `Estimate ± SE`, t, p)


#this is the smooth table
smooth <- as.data.frame(summary(m_gam)$s.table)

smooth$Term <- rownames(smooth)

smooth_pub <- smooth %>%
  dplyr::mutate(
    edf = round(edf, 2),
    F = round(F, 2),
    p = ifelse(`p-value` < 0.001, "<0.001", round(`p-value`, 3))
  ) %>%
  dplyr::select(Term, edf, F, p)


param_pub$Term <- gsub("group", "", param_pub$Term)

smooth_pub$Term <- gsub("s\\(Temp\\):group", "Temp × ", smooth_pub$Term)



```
Plotting
```{r}
#library(gratia)

# # Compact: one panel per group showing the temperature effect
# draw(m_gam)
# 
# # Or: predictions on a grid with CIs for publication-quality overlays
# library(dplyr)
# 
# nd <- tidyr::expand_grid(
#   Temp  = seq(min(data$Temp, na.rm=TRUE), max(data$Temp, na.rm=TRUE), length.out = 200),
#   Nutrients     = levels(data$Nutrients),
#   Predation     = levels(data$Predation)
# ) |>
#   mutate(group = interaction(Nutrients, Predation, drop = TRUE))
# 
# pr <- predict(m_gam, newdata = nd, se.fit = TRUE, type = "response")
# nd$fit <- pr$fit
# nd$lo  <- pr$fit - 1.96*pr$se.fit
# nd$hi  <- pr$fit + 1.96*pr$se.fit
# 
# # ggplot overlay (optional)
# # library(ggplot2)
#  ggplot(nd, aes(Temp, fit, color = group, fill = group)) +
#    geom_line(size = 1) +
#    geom_ribbon(aes(ymin = lo, ymax = hi), alpha = 0.15, color = NA) +
#    labs(y = "Predicted cells") +
#    theme_bw()
# 
# #It gives me something very similar to a TPCs
```
So yeah...there is a lot of interactions. Maybe emmeans so I can do post-hoc pair comparisons ?

```{r}
library(emmeans)

# Define the exact temperatures at which you want comparisons
Temps <- sort(unique(data$Temp))  # your six temps

# Get estimated marginal means for group at each temp (marginal over nothing else)
emm_grp_by_temp <- emmeans(
  m_gam,
  specs = ~ group | Temp,        # group means, separated by temperature
  at    = list(Temp = Temps),    # evaluate exactly at your six temps
  type  = "response"             # on the response (not link) scale
)

# Pairwise comparisons among all 4 groups at each temperature for abundance
pairs_grp_by_temp <- contrast(emm_grp_by_temp, method = "pairwise", adjust = "holm")
pairs_grp_by_temp

#emm_df <- as.data.frame(pairs_grp_by_temp)
```
Turning emmeans results into a table for excel

```{r}
df <- as.data.frame(pairs_grp_by_temp)

library(tidyr)

df_clean <- df %>%
  separate(contrast, into = c("Group1", "Group2"), sep = " - ")


df_clean <- df_clean %>%
  separate(Group1, into = c("Nutrients1", "Predation1"), sep = "\\.") %>%
  separate(Group2, into = c("Nutrients2", "Predation2"), sep = "\\.")

df_clean <- df_clean %>%
  mutate(
    estimate = round(estimate, 3),
    SE = round(SE, 3),
    t.ratio = round(t.ratio, 2),
    p.value = ifelse(p.value < 0.001, "<0.001", round(p.value, 3))
  )

df_clean 

library(knitr)
library(kableExtra)

df_clean_table <-df_clean %>%
  kable(caption = "Pairwise comparisons of treatments within each temperature") %>%
  kable_styling(full_width = FALSE)
df_clean_table



df_table_2 <- df_clean %>%
  select(Temp,
         Nutrients1, Predation1,
         Nutrients2, Predation2,
         estimate, SE, t.ratio, p.value)


write.csv(df_table_2, "emmeans_table.csv", row.names = FALSE)

## Another method
# colnames(df_clean)
# 
# df_clean <- df %>%
#   separate(contrast, into = c("Group1", "Group2"), sep = " - ", extra = "merge")
# 
# df_pub <- df_clean %>%
#   mutate(
#     Comparison = paste(Group1, "vs", Group2),
#     `Estimate ± SE` = paste0(estimate, " ± ", SE)
#   ) %>%
#   select(Temp, Comparison, `Estimate ± SE`, t.ratio, p.value)
# 
# df_pub
```



## Comparing growth rate
Doing the same with growth rate
```{r}
sum_pred<-data %>%
  group_by(Temp, Nutrients, Predation) %>%
  summarise(mean=mean(r), sd=sd(r), #summarizing abundance 
            n=n()) %>% #summarizing richness
  mutate(se=sd/sqrt(n))

sum_pred
```

### Plotting effect nutrients and predation on Tetra growth rate across temperatures
```{r}

pd <- position_dodge(width = 0.85)

ggplot() + #calling ggplot
  geom_point(data=sum_pred, aes(x=Temp, y=mean, color=Nutrients, shape=Predation, group = interaction(Nutrients, Predation)), 
             size = 2.5, position = pd)+
  geom_errorbar(data=sum_pred, aes(x=Temp, ymin=mean-se, ymax=mean+se, group = interaction(Nutrients, Predation), color=Nutrients),  
               size = 0.6, width = 0.2, alpha = 0.6, position = pd)+
  geom_point(data=data, aes(x=Temp, y=r, color=Nutrients, shape=Predation, group = interaction(Nutrients, Predation)),
               size = 1, position = pd, alpha=0.2)+
    #geom_point(data=data, aes(x=Temp, y=Cells, color=Nutrients, shape=Predation),
     #          size = 2, position = position_dodge(width = 0.85), alpha=0.4)+ #plotting 
  #ploting SE
  theme_classic()+ # a more classic look
     theme(#panel.border = element_rect(colour = "black"),
           legend.position =c(0.10, 0.45),
         axis.text.x = element_text(size = 10                          #margin = margins(t = 10, b = 5)
                                    ), 
        # axis.title.x = element_blank(), 
         axis.title.y = element_text(size = 12, hjust = 0.6, vjust = 2.5), 
         axis.text.y = element_text(size = 11), 
       #  legend.position ="none",
         strip.text = element_text(color = "black", face="bold", size = 15, hjust =0.2),
        # axis.line.x.top = element_blank(),
    #axis.line.y.right = element_blank(),
    strip.background = element_rect(fill = "white", color = "white"))+
  ylab("Population growth rate (r)")+
 xlab("Temperature (°C)")+
  scale_x_continuous(breaks = seq(14, 32, by = 2))+
  scale_colour_manual(values = c("High Nutrients"="#D55E00", "Low Nutrients"="#0072B2")) 

ggsave("NutPredTPC_Tetra_r.png", height = 13, width = 20, units = 'cm', dpi= 300, type = "cairo")
```

Modelling and testing differences using a linear model (probably not correct)
```{r}
lm<- lm(r~Temp*Nutrients*Predation, data=data)
summary(lm)

#str(data)
#g<-glmer(r~Nutrients:Predation:Temp, data=data)

#g<-gls(r~Nutrients:Predation:Temp, data=data)

library(nlme)

#g<-gls(r~Nutrients +Temp+Predation, data=data)
#summary(g)

```
Modelling the effect of the factors on growth rate considering a non linear model (GAMM)
```{r}
str(data)

data$Nutrients<-(factor(data$Nutrients))
data$Predation<-(factor(data$Predation))

data$group <- interaction(data$Nutrients, data$Predation, drop = TRUE)
# levels will look like: "low.no", "high.no", "low.yes", "high.yes"

# --- Model: group-specific smooths of temperature + group intercepts
library(mgcv)
m_gam_r <- gam(
  r ~ group + s(Temp, by = group, k = 6, bs = "cr"),
  method = "REML",
  data = data
)

summary(m_gam_r)
#gam.check(m_gam_r)
```
Comparing using emmeans
```{r}
# Define the exact temperatures at which you want comparisons
Temps <- sort(unique(data$Temp))  # your six temps

# Get estimated marginal means for group at each temp (marginal over nothing else)
emm_grp_by_temp_r <- emmeans(
  m_gam_r,
  specs = ~ group | Temp,        # group means, separated by temperature
  at    = list(Temp = Temps),    # evaluate exactly at your six temps
  type  = "response"             # on the response (not link) scale
)

# Pairwise comparisons among all 4 groups at each temperature
pairs_grp_by_temp_r <- contrast(emm_grp_by_temp_r, method = "pairwise", adjust = "holm")
pairs_grp_by_temp_r


##Turning emmeans results into a table for excel

df <- as.data.frame(pairs_grp_by_temp_r)
library(tidyr)

df_clean <- df %>%
  separate(contrast, into = c("Group1", "Group2"), sep = " - ")


df_clean <- df_clean %>%
  separate(Group1, into = c("Nutrients1", "Predation1"), sep = "\\.") %>%
  separate(Group2, into = c("Nutrients2", "Predation2"), sep = "\\.")

df_clean <- df_clean %>%
  mutate(
    estimate = round(estimate, 3),
    SE = round(SE, 3),
    t.ratio = round(t.ratio, 2),
    p.value = ifelse(p.value < 0.001, "<0.001", round(p.value, 3))
  )

df_clean 

library(knitr)
library(kableExtra)

df_clean_table <-df_clean %>%
  kable(caption = "Pairwise comparisons of treatments within each temperature") %>%
  kable_styling(full_width = FALSE)
df_clean_table



df_table_2 <- df_clean %>%
  select(Temp,
         Nutrients1, Predation1,
         Nutrients2, Predation2,
         estimate, SE, t.ratio, p.value)


write.csv(df_table_2, "emmeans_table_r.csv", row.names = FALSE)
```


## TPC comparing across treatments nutrients and no nutrients (Gaussian fitting)
### High Nutrients and No predation
```{r}
d<-read.csv(file="exp1.csv", header=TRUE)
#d$Species=as.factor(d$Species)
str(d)
d$T<-d$Temp+273

d<-d%>%
  filter(Nutrients=="High Nutrients" & Predation=="No")

# fitting a lactin model
fit_gaussian_resp<-nls_multstart(r~
                          gaussian_1987(temp = T, rmax, topt, a), 
          data=d,
           iter = c(4, 4, 4),
          start_lower=get_start_vals(d$T, d$r, model_name = 'gaussian_1987')-10,
          start_upper=get_start_vals(d$T, d$r, model_name = 'gaussian_1987')+10,
          lower=get_lower_lims(d$T, d$r, model_name = 'gaussian_1987'),
          upper=get_upper_lims(d$T, d$r, model_name = 'gaussian_1987'),
          supp_errors = 'Y',
            convergence_count = FALSE) # this is my previous fitting for predation 

# Creating predictions
newT <- data.frame(T = seq(min(d$T-5), max(d$T+5), length.out=100))
newT$pred <- predict(fit_gaussian_resp, newdata = newT)
newTHn<-newT

#summary of model and calculation parameters 
summary(fit_gaussian_resp)

params<-rTPC::calc_params(fit_gaussian_resp)
toptHn<-params$topt
params


fit_gaussian_resp_nlsLM<-minpack.lm::nlsLM(r~
                                            gaussian_1987(temp = T, rmax, topt, a), 
          data=d,
          start = coef(fit_gaussian_resp), #I just add the coeficient from my previously calculated model 
                        lower = get_lower_lims(d$T, d$r, model_name = 'gaussian_1987'),
                        upper = get_upper_lims(d$T, d$r, model_name = 'gaussian_1987'),
                        weights = rep(1, times = nrow(d)))

summary(fit_gaussian_resp_nlsLM)
```

Boot strapping

```{r}
# bootstrap using case resampling
boot1 <- Boot(fit_gaussian_resp_nlsLM, method = 'case')

#hist(boot1, layout = c(2,2))

boot1_preds <- boot1$t %>%
  as.data.frame() %>%
  drop_na() %>%
  mutate(iter = 1:n()) %>%
  group_by_all() %>%
  do(data.frame(T = seq(min(d$T-5), max(d$T+5), length.out = 100))) %>%
  ungroup() %>%
  mutate(pred = gaussian_1987(temp = T, rmax, topt, a))

# calculate bootstrapped confidence intervals
boot1_conf_predsHn <- group_by(boot1_preds, T) %>%
  summarise(conf_lower = quantile(pred, 0.025),
            conf_upper = quantile(pred, 0.975)) %>%
  ungroup()

CI_Hn<-boot1_conf_predsHn

# Predation prediction with bootstraping interval confidences
ggplot() +
  geom_line(aes(T-273, pred), newTHn, col = 'blue') +
  geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper), boot1_conf_predsHn, fill = 'blue', alpha = 0.3) +
  geom_point(aes(T-273, r), d, size = 1, alpha = 0.5, position="jitter") +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       y = 'Respiration rates',
       title = 'Growth rate with low nutrients and no predation')+
  ylim(0, 9)

```

### Low Nutrients and No predation
```{r}
d<-read.csv(file="exp1.csv", header=TRUE)
#d$Species=as.factor(d$Species)
str(d)
d$T<-d$Temp+273

d<-d%>%
  filter(Nutrients=="Low Nutrients" & Predation=="No")

# fitting a Gaussian model
fit_gaussian_resp<-nls_multstart(r~
                          gaussian_1987(temp = T, rmax, topt, a), 
          data=d,
           iter = c(4, 4, 4),
          start_lower=get_start_vals(d$T, d$r, model_name = 'gaussian_1987')-10,
          start_upper=get_start_vals(d$T, d$r, model_name = 'gaussian_1987')+10,
          lower=get_lower_lims(d$T, d$r, model_name = 'gaussian_1987'),
          upper=get_upper_lims(d$T, d$r, model_name = 'gaussian_1987'),
          supp_errors = 'Y',
            convergence_count = FALSE) # this is my previous fitting for predation 

# Creating predictions
newT <- data.frame(T = seq(min(d$T-5), max(d$T+5), length.out=100))
newT$pred <- predict(fit_gaussian_resp, newdata = newT)
newTLn<-newT

#summary of model and calculation parameters 
summary(fit_gaussian_resp)

params<-rTPC::calc_params(fit_gaussian_resp)
toptLn<-params$topt
params


fit_gaussian_resp_nlsLM<-minpack.lm::nlsLM(r~
                                            gaussian_1987(temp = T, rmax, topt, a), 
          data=d,
          start = coef(fit_gaussian_resp), #I just add the coeficient from my previously calculated model 
                        lower = get_lower_lims(d$T, d$r, model_name = 'gaussian_1987'),
                        upper = get_upper_lims(d$T, d$r, model_name = 'gaussian_1987'),
                        weights = rep(1, times = nrow(d)))

summary(fit_gaussian_resp_nlsLM)
```

Boot strapping
```{r}
# bootstrap using case resampling
boot1 <- Boot(fit_gaussian_resp_nlsLM, method = 'case')

#hist(boot1, layout = c(2,2))

boot1_preds <- boot1$t %>%
  as.data.frame() %>%
  drop_na() %>%
  mutate(iter = 1:n()) %>%
  group_by_all() %>%
  do(data.frame(T = seq(min(d$T-5), max(d$T+5), length.out = 100))) %>%
  ungroup() %>%
  mutate(pred = gaussian_1987(temp = T, rmax, topt, a))

# calculate bootstrapped confidence intervals
boot1_conf_predsLn <- group_by(boot1_preds, T) %>%
  summarise(conf_lower = quantile(pred, 0.025),
            conf_upper = quantile(pred, 0.975)) %>%
  ungroup()

CI_Ln<-boot1_conf_predsLn

# Predation prediction with bootstraping interval confidences
ggplot() +
  geom_line(aes(T-273, pred), newTLn, col = 'blue') +
  geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper), boot1_conf_predsLn, fill = 'blue', alpha = 0.3) +
  geom_point(aes(T-273, r), d, size = 1, alpha = 0.5, position="jitter") +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       y = 'Respiration rates',
       title = 'Growth rate with low nutrients and no predation')+
  ylim(0, 9)

```

Combining nutrients and no nutrients
```{r}
d<-read.csv(file="exp1.csv", header=TRUE)

ggplot() +
  geom_line(aes(T-273, pred), newTHn, col = '#F39B7FB2') +
  geom_line(aes(T-273, pred), newTLn, col = '#00A087FF') +
  geom_point(aes(T-273, r, color=Nutrients), d, size = 1, alpha = 0.5, position="jitter")+         geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper), CI_Hn, fill = '#F39B7FB2', alpha = 0.3) +
  geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper),CI_Ln, fill = '#00A087FF', alpha = 0.3) +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       y = 'Growth rate (r)')+
  scale_y_continuous(limits=c(-0.5, 10))+
scale_x_continuous(limits=c(10, 34), breaks=seq(10, 34, 2))+
  theme(legend.position = c(0.15, 0.88),
         legend.key.spacing.y = unit(0.5, "cm"),
         legend.text = element_text(size = 12),
         panel.grid.major = element_blank(), 
         panel.grid.minor = element_blank(), 
         panel.background = element_rect(colour="white"), 
         panel.border = element_blank(),
         axis.line = element_line(colour = "black"),
         #axis.line.x.top = element_line(colour="black"),
         #axis.line.y.right = element_line(colour="black"),
         #axis.line.y.left = element_line(colour="black"),
         strip.background=element_rect(colour="white", fill="white"),
         strip.text = element_text(face = "italic", color = "black", size = 13, hjust =0.05))
#+
#  scale_colour_manual(name = "", values =c(V.melones="#00A087FF", 
 ##labels= c(V.melones=expression(italic("V.melones")),                                                        C.haemastoma=expression(italic("C.haemastoma")),                                                                E.pyrostoma=expression(italic("E.pyrostoma"))))

ggsave("TPC_Nutrients.png", height = 12, width = 20, units = 'cm', dpi= 300, type = "cairo")
```

## TPCs comparing all factors
### High nutrients and predation present
```{r}
d<-read.csv(file="exp1.csv", header=TRUE)
#d$Species=as.factor(d$Species)
str(d)
d$T<-d$Temp+273

d<-d%>%
  filter(Nutrients=="High Nutrients" & Predation=="Yes")

# fitting a lactin model
fit_gaussian_resp<-nls_multstart(r~
                          gaussian_1987(temp = T, rmax, topt, a), 
          data=d,
           iter = c(4, 4, 4),
          start_lower=get_start_vals(d$T, d$r, model_name = 'gaussian_1987')-10,
          start_upper=get_start_vals(d$T, d$r, model_name = 'gaussian_1987')+10,
          lower=get_lower_lims(d$T, d$r, model_name = 'gaussian_1987'),
          upper=get_upper_lims(d$T, d$r, model_name = 'gaussian_1987'),
          supp_errors = 'Y',
            convergence_count = FALSE) # this is my previous fitting for predation 

# Creating predictions
newT <- data.frame(T = seq(min(d$T-5), max(d$T+5), length.out=100))
newT$pred <- predict(fit_gaussian_resp, newdata = newT)
newTHnPp<-newT

#summary of model and calculation parameters 
summary(fit_gaussian_resp)

params<-rTPC::calc_params(fit_gaussian_resp)
toptHnPp<-params$topt
params


fit_gaussian_resp_nlsLM<-minpack.lm::nlsLM(r~
                                            gaussian_1987(temp = T, rmax, topt, a), 
          data=d,
          start = coef(fit_gaussian_resp), #I just add the coeficient from my previously calculated model 
                        lower = get_lower_lims(d$T, d$r, model_name = 'gaussian_1987'),
                        upper = get_upper_lims(d$T, d$r, model_name = 'gaussian_1987'),
                        weights = rep(1, times = nrow(d)))

summary(fit_gaussian_resp_nlsLM)
```

Boot strapping
```{r}
# bootstrap using case resampling
boot1 <- Boot(fit_gaussian_resp_nlsLM, method = 'case')

#hist(boot1, layout = c(2,2))

boot1_preds <- boot1$t %>%
  as.data.frame() %>%
  drop_na() %>%
  mutate(iter = 1:n()) %>%
  group_by_all() %>%
  do(data.frame(T = seq(min(d$T-5), max(d$T+5), length.out = 100))) %>%
  ungroup() %>%
  mutate(pred = gaussian_1987(temp = T, rmax, topt, a))

# calculate bootstrapped confidence intervals
boot1_conf_predsHnPp <- group_by(boot1_preds, T) %>%
  summarise(conf_lower = quantile(pred, 0.025),
            conf_upper = quantile(pred, 0.975)) %>%
  ungroup()

CI_HnPp<-boot1_conf_predsHnPp

# Predation prediction with bootstraping interval confidences
ggplot() +
  geom_line(aes(T-273, pred), newTHnPp, col = 'blue') +
  geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper), boot1_conf_predsHnPp, fill = 'blue', alpha = 0.3) +
  geom_point(aes(T-273, r), d, size = 1, alpha = 0.5, position="jitter") +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       y = 'Respiration rates',
       title = 'Growth rate with high nutrients and predation')+
  ylim(0, 9)

```

### Low nutrients and predation present
```{r}
d<-read.csv(file="exp1.csv", header=TRUE)
#d$Species=as.factor(d$Species)
str(d)
d$T<-d$Temp+273

d<-d%>%
  filter(Nutrients=="Low Nutrients" & Predation=="Yes")

# fitting a lactin model
fit_gaussian_resp<-nls_multstart(r~
                          gaussian_1987(temp = T, rmax, topt, a), 
          data=d,
           iter = c(4, 4, 4),
          start_lower=get_start_vals(d$T, d$r, model_name = 'gaussian_1987')-10,
          start_upper=get_start_vals(d$T, d$r, model_name = 'gaussian_1987')+10,
          lower=get_lower_lims(d$T, d$r, model_name = 'gaussian_1987'),
          upper=get_upper_lims(d$T, d$r, model_name = 'gaussian_1987'),
          supp_errors = 'Y',
            convergence_count = FALSE) # this is my previous fitting for predation 

# Creating predictions
newT <- data.frame(T = seq(min(d$T-5), max(d$T+5), length.out=100))
newT$pred <- predict(fit_gaussian_resp, newdata = newT)
newTLnPp<-newT

#summary of model and calculation parameters 
summary(fit_gaussian_resp)

params<-rTPC::calc_params(fit_gaussian_resp)
toptLnPp<-params$topt
params

fit_gaussian_resp_nlsLM<-minpack.lm::nlsLM(r~
                                            gaussian_1987(temp = T, rmax, topt, a), 
          data=d,
          start = coef(fit_gaussian_resp), #I just add the coeficient from my previously calculated model 
                        lower = get_lower_lims(d$T, d$r, model_name = 'gaussian_1987'),
                        upper = get_upper_lims(d$T, d$r, model_name = 'gaussian_1987'),
                        weights = rep(1, times = nrow(d)))

summary(fit_gaussian_resp_nlsLM)
```

Boot strapping
```{r}
# bootstrap using case resampling
boot1 <- Boot(fit_gaussian_resp_nlsLM, method = 'case')

#hist(boot1, layout = c(2,2))

boot1_preds <- boot1$t %>%
  as.data.frame() %>%
  drop_na() %>%
  mutate(iter = 1:n()) %>%
  group_by_all() %>%
  do(data.frame(T = seq(min(d$T-5), max(d$T+5), length.out = 100))) %>%
  ungroup() %>%
  mutate(pred = gaussian_1987(temp = T, rmax, topt, a))

# calculate bootstrapped confidence intervals
boot1_conf_predsLnPp <- group_by(boot1_preds, T) %>%
  summarise(conf_lower = quantile(pred, 0.025),
            conf_upper = quantile(pred, 0.975)) %>%
  ungroup()

CI_LnPp<-boot1_conf_predsLnPp

# Predation prediction with bootstraping interval confidences
ggplot() +
  geom_line(aes(T-273, pred), newTLnPp, col = 'blue') +
  geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper), boot1_conf_predsLn, fill = 'blue', alpha = 0.3) +
  geom_point(aes(T-273, r), d, size = 1, alpha = 0.5, position="jitter") +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       y = 'Respiration rates',
       title = 'Growth rate with low nutrients and predation present')+
  ylim(0, 9)

```

### TPCs Combining nutrients predation
```{r}
d<-read.csv(file="exp1.csv", header=TRUE)

ggplot() +
  geom_line(aes(T-273, pred), newTHn, col = '#00A087FF', size=0.7) +
  geom_line(aes(T-273, pred), newTLn, col = '#F39B7FB2', size=0.7) +
  geom_line(aes(T-273, pred), newTHnPp, col = 'darkgreen', size=0.7) +
  geom_line(aes(T-273, pred), newTLnPp, col = 'lightsalmon4', size=0.7) +
  geom_point(aes(Temp, r, color=Nutrients, shape=Predation), d, size = 1.5, alpha = 0.5, position="jitter")+         
  geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper), CI_Hn, fill = '#00A087FF', alpha = 0.2) +
  geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper),CI_Ln, fill = 'lightsalmon4', alpha = 0.2) +
  geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper), CI_HnPp, fill = 'darkgreen', alpha = 0.2) +
  geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper),CI_LnPp, fill = 'red', alpha = 0.2) +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       y = 'Growth rate (r)')+
  scale_y_continuous(limits=c(-0.2, 9))+
scale_x_continuous(limits=c(10, 38), breaks=seq(10, 38, 2))+
  theme(legend.position = c(0.15, 0.75),
         legend.key.spacing.y = unit(0.5, "cm"),
         legend.text = element_text(size = 12),
         panel.grid.major = element_blank(), 
         panel.grid.minor = element_blank(), 
         panel.background = element_rect(colour="white"), 
         panel.border = element_blank(),
         axis.line = element_line(colour = "black"),
         #axis.line.x.top = element_line(colour="black"),
         #axis.line.y.right = element_line(colour="black"),
         #axis.line.y.left = element_line(colour="black"),
         strip.background=element_rect(colour="white", fill="white"),
         strip.text = element_text(face = "italic", 
                                   color = "black", size = 13, hjust =0.05))+
          scale_colour_manual(name = "", 
 values =c('High Nutrients'="#00A087FF", 'Low Nutrients'="#F39B7FB2"), 
 labels= c('High Nutrients'="High Nutrients", 'Low Nutrients'="Low Nutrients"))+
  geom_vline(xintercept=toptHn-273, linetype="dashed", size=0.5, color="#00A087FF")+
  geom_vline(xintercept=toptLn-273, linetype="dashed", size=0.5, color="#F39B7FB2")+
  geom_vline(xintercept=toptHnPp-273, linetype="dashed", size=0.5, color="darkgreen")+
  geom_vline(xintercept=toptLnPp-273, linetype="dashed", size=0.5, color="lightsalmon4")


ggsave("TPC_combined.png", height = 12, width = 20, units = 'cm', dpi= 300, type = "cairo")
```

```{r}
d<-read.csv(file="exp1.csv", header=TRUE)
str(d)

ggplot() +
  geom_line(aes(T-273, pred), newTHn, col = '#00A087FF', size=0.7) +
  geom_line(aes(T-273, pred), newTLn, col = '#F39B7FB2', size=0.7) +
  geom_line(aes(T-273, pred), newTHnPp, col = 'darkgreen', size=0.7) +
  geom_line(aes(T-273, pred), newTLnPp, col = 'lightsalmon4', size=0.7) +
  geom_point(aes(Temp, r, color=Cat), d, size = 1.5, alpha = 0.5)+ 
  #position="jitter"        
  geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper), CI_Hn, fill = '#00A087FF', alpha = 0.2) +
  geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper),CI_Ln, fill = 'lightsalmon4', alpha = 0.2) +
  geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper), CI_HnPp, fill = 'darkgreen', alpha = 0.2) +
  geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper),CI_LnPp, fill = 'red', alpha = 0.2) +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       y = 'Growth rate (r)')+
  scale_y_continuous(limits=c(-0.2, 9))+
scale_x_continuous(limits=c(10, 38), breaks=seq(10, 38, 2))+
  theme(legend.position = c(0.17, 0.75),
         legend.key.spacing.y = unit(0.3, "cm"),
         legend.text = element_text(size = 10.5),
         panel.grid.major = element_blank(), 
         panel.grid.minor = element_blank(), 
         panel.background = element_rect(colour="white"), 
         panel.border = element_blank(),
         axis.line = element_line(colour = "black"),
         #axis.line.x.top = element_line(colour="black"),
         #axis.line.y.right = element_line(colour="black"),
         #axis.line.y.left = element_line(colour="black"),
         strip.background=element_rect(colour="white", fill="white"),
         strip.text = element_text(face = "italic", 
                                   color = "black", size = 13, hjust =0.05))+
          scale_colour_manual(name = "", 
 values =c('High NutrientsNo'="#00A087FF", 'High NutrientsYes'="darkgreen", 'Low NutrientsNo'="#F39B7FB2", 'Low NutrientsYes'="lightsalmon4"), 
 labels= c('High NutrientsNo'="High Nutrients/No predation", 'Low NutrientsNo'="Low Nutrients/No predation", 'High NutrientsYes'="High Nutrients/Predation", 'Low NutrientsYes'="Low Nutrients/Predation"))+
  geom_vline(xintercept=toptHn-273, linetype="dashed", size=0.5, color="#00A087FF")+
  geom_vline(xintercept=toptLn-273, linetype="dashed", size=0.5, color="#F39B7FB2")+
  geom_vline(xintercept=toptHnPp-273, linetype="dashed", size=0.5, color="darkgreen")+
  geom_vline(xintercept=toptLnPp-273, linetype="dashed", size=0.5, color="lightsalmon4")


ggsave("TPC_combined2.png", height = 13, width = 20, units = 'cm', dpi= 300, type = "cairo")
```

## TPC comparing across treatments nutrients and no nutrients (Schoolfield model)
### High Nutrients and No predation
```{r}
d<-read.csv(file="exp1.csv", header=TRUE)
#d$Species=as.factor(d$Species)
str(d)
d$T<-d$Temp+273

d<-d%>%
  filter(Nutrients=="High Nutrients" & Predation=="No")

start_vals <- get_start_vals(d$T, d$r, model_name = 'sharpeschoolfull_1981')

# fitting a lactin model
fit_schoolfield_resp<-nls_multstart(r~sharpeschoolfull_1981(temp = T, r_tref, e, el, tl, eh, th, tref = 20),
data = d,
iter = c(3,3,3,3,3,3),
start_lower = start_vals - 10,
start_upper = start_vals + 10,
lower = get_lower_lims(d$T, d$r, model_name = 'sharpeschoolfull_1981'),
upper = get_upper_lims(d$T, d$r, model_name = 'sharpeschoolfull_1981'),
supp_errors = 'Y',
convergence_count = FALSE) 

# Creating predictions
newT <- data.frame(T = seq(min(d$T-5), max(d$T+5), length.out=100))
newT$pred <- predict(fit_schoolfield_resp, newdata = newT)
newTHn<-newT

#summary of model and calculation parameters 
summary(fit_schoolfield_resp)

params<-rTPC::calc_params(fit_schoolfield_resp)
toptHn<-params$topt
params


fit_schoolfield_resp_nlsLM<-minpack.lm::nlsLM(r~sharpeschoolfull_1981(temp = T, r_tref, e, el, tl, eh, th, tref = 20), 
          data=d,
          start = coef(fit_schoolfield_resp), #I just add the coeficient from my previously calculated model 
                        lower = get_lower_lims(d$T, d$r, model_name = 'sharpeschoolfull_1981'),
                        upper = get_upper_lims(d$T, d$r, model_name = 'sharpeschoolfull_1981'),
                        weights = rep(1, times = nrow(d)))

summary(fit_schoolfield_resp_nlsLM)
```

Boot strapping

```{r}
# bootstrap using case resampling
boot1 <- Boot(fit_schoolfield_resp_nlsLM, method = 'case')

#hist(boot1, layout = c(2,2))

boot1_preds <- boot1$t %>%
  as.data.frame() %>%
  drop_na() %>%
  mutate(iter = 1:n()) %>%
  group_by_all() %>%
  do(data.frame(T = seq(min(d$T-5), max(d$T+5), length.out = 100))) %>%
  ungroup() %>%
  mutate(pred = sharpeschoolfull_1981(temp = T, r_tref, e, el, tl, eh, th, tref = 20))

# calculate bootstrapped confidence intervals
boot1_conf_predsHn <- group_by(boot1_preds, T) %>%
  summarise(conf_lower = quantile(pred, 0.025),
            conf_upper = quantile(pred, 0.975)) %>%
  ungroup()

CI_Hn<-boot1_conf_predsHn

# Predation prediction with bootstraping interval confidences
ggplot() +
  geom_line(aes(T-273, pred), newTHn, col = 'blue') +
  geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper), boot1_conf_predsHn, fill = 'blue', alpha = 0.3) +
  geom_point(aes(T-273, r), d, size = 1, alpha = 0.5, position="jitter") +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       y = 'Respiration rates',
       title = 'Growth rate with low nutrients and no predation')+
  ylim(0, 9)

```

### Low Nutrients and No predation
```{r}
d<-read.csv(file="exp1.csv", header=TRUE)
#d$Species=as.factor(d$Species)
str(d)
d$T<-d$Temp+273

d<-d%>%
  filter(Nutrients=="Low Nutrients" & Predation=="No")

start_vals <- get_start_vals(d$T, d$r, model_name = 'sharpeschoolfull_1981')

# fitting a schoolfield model
fit_schoolfield_resp<-nls_multstart(r~sharpeschoolfull_1981(temp = T, r_tref, e, el, tl, eh, th, tref = 20),
data = d,
iter = c(3,3,3,3,3,3),
start_lower = start_vals - 10,
start_upper = start_vals + 10,
lower = get_lower_lims(d$T, d$r, model_name = 'sharpeschoolfull_1981'),
upper = get_upper_lims(d$T, d$r, model_name = 'sharpeschoolfull_1981'),
supp_errors = 'Y',
convergence_count = FALSE) 

# Creating predictions
newT <- data.frame(T = seq(min(d$T-5), max(d$T+5), length.out=100))
newT$pred <- predict(fit_schoolfield_resp, newdata = newT)
newTLn<-newT

#summary of model and calculation parameters 
summary(fit_schoolfield_resp)

params<-rTPC::calc_params(fit_schoolfield_resp)
toptLn<-params$topt
params

fit_schoolfield_resp_nlsLM<-minpack.lm::nlsLM(r~sharpeschoolfull_1981(temp = T, r_tref, e, el, tl, eh, th, tref = 20), 
          data=d,
          start = coef(fit_schoolfield_resp), #I just add the coeficient from my previously calculated model 
                        lower = get_lower_lims(d$T, d$r, model_name = 'sharpeschoolfull_1981'),
                        upper = get_upper_lims(d$T, d$r, model_name = 'sharpeschoolfull_1981'),
                        weights = rep(1, times = nrow(d)))

summary(fit_schoolfield_resp_nlsLM)
```

Boot strapping
```{r}
# bootstrap using case resampling
boot1 <- Boot(fit_schoolfield_resp_nlsLM, method = 'case')

#hist(boot1, layout = c(2,2))

boot1_preds <- boot1$t %>%
  as.data.frame() %>%
  drop_na() %>%
  mutate(iter = 1:n()) %>%
  group_by_all() %>%
  do(data.frame(T = seq(min(d$T-5), max(d$T+5), length.out = 100))) %>%
  ungroup() %>%
  mutate(pred = sharpeschoolfull_1981(temp = T, r_tref, e, el, tl, eh, th, tref = 20))

# calculate bootstrapped confidence intervals
boot1_conf_predsLn <- group_by(boot1_preds, T) %>%
  summarise(conf_lower = quantile(pred, 0.025),
            conf_upper = quantile(pred, 0.975)) %>%
  ungroup()

CI_Ln<-boot1_conf_predsLn

# Predation prediction with bootstraping interval confidences
ggplot() +
  geom_line(aes(T-273, pred), newTLn, col = 'blue') +
  geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper), boot1_conf_predsLn, fill = 'blue', alpha = 0.3) +
  geom_point(aes(T-273, r), d, size = 1, alpha = 0.5, position="jitter") +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       y = 'Respiration rates',
       title = 'Growth rate with low nutrients and no predation')+
  ylim(0, 9)

```

Combining nutrients and no nutrients
```{r}
d<-read.csv(file="exp1.csv", header=TRUE)

ggplot() +
  geom_line(aes(T-273, pred), newTHn, col = '#F39B7FB2') +
  geom_line(aes(T-273, pred), newTLn, col = '#00A087FF') +
  geom_point(aes(T-273, r, color=Nutrients), d, size = 1, alpha = 0.5, position="jitter")+         geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper), CI_Hn, fill = '#F39B7FB2', alpha = 0.3) +
  geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper),CI_Ln, fill = '#00A087FF', alpha = 0.3) +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       y = 'Growth rate (r)')+
  scale_y_continuous(limits=c(-0.5, 10))+
scale_x_continuous(limits=c(10, 34), breaks=seq(10, 34, 2))+
  theme(legend.position = c(0.15, 0.88),
         legend.key.spacing.y = unit(0.5, "cm"),
         legend.text = element_text(size = 12),
         panel.grid.major = element_blank(), 
         panel.grid.minor = element_blank(), 
         panel.background = element_rect(colour="white"), 
         panel.border = element_blank(),
         axis.line = element_line(colour = "black"),
         #axis.line.x.top = element_line(colour="black"),
         #axis.line.y.right = element_line(colour="black"),
         #axis.line.y.left = element_line(colour="black"),
         strip.background=element_rect(colour="white", fill="white"),
         strip.text = element_text(face = "italic", color = "black", size = 13, hjust =0.05))
#+
#  scale_colour_manual(name = "", values =c(V.melones="#00A087FF", 
 ##labels= c(V.melones=expression(italic("V.melones")),                                                        C.haemastoma=expression(italic("C.haemastoma")),                                                                E.pyrostoma=expression(italic("E.pyrostoma"))))

ggsave("TPC_Nutrients.png", height = 12, width = 20, units = 'cm', dpi= 300, type = "cairo")
```

## TPCs comparing all factors (Schoolfield)
### High nutrients and predation present
```{r}
d<-read.csv(file="exp1.csv", header=TRUE)
#d$Species=as.factor(d$Species)
str(d)
d$T<-d$Temp+273

d<-d%>%
  filter(Nutrients=="High Nutrients" & Predation=="Yes")

start_vals <- get_start_vals(d$T, d$r, model_name = 'sharpeschoolfull_1981')


# fitting a lactin model
fit_schoolfield_resp<-nls_multstart(r~sharpeschoolfull_1981(temp = T, r_tref, e, el, tl, eh, th, tref = 20),
data = d,
iter = c(3,3,3,3,3,3),
start_lower = start_vals - 10,
start_upper = start_vals + 10,
lower = get_lower_lims(d$T, d$r, model_name = 'sharpeschoolfull_1981'),
upper = get_upper_lims(d$T, d$r, model_name = 'sharpeschoolfull_1981'),
supp_errors = 'Y',
convergence_count = FALSE) 

# Creating predictions
newT <- data.frame(T = seq(min(d$T-5), max(d$T+5), length.out=100))
newT$pred <- predict(fit_schoolfield_resp, newdata = newT)
newTHnPp<-newT

#summary of model and calculation parameters 
summary(fit_schoolfield_resp)

params<-rTPC::calc_params(fit_schoolfield_resp)
toptHnPp<-params$topt
params


fit_schoolfield_resp_nlsLM<-minpack.lm::nlsLM(r~sharpeschoolfull_1981(temp = T, r_tref, e, el, tl, eh, th, tref = 20), 
          data=d,
          start = coef(fit_schoolfield_resp), #I just add the coeficient from my previously calculated model 
                        lower = get_lower_lims(d$T, d$r, model_name = 'sharpeschoolfull_1981'),
                        upper = get_upper_lims(d$T, d$r, model_name = 'sharpeschoolfull_1981'),
                        weights = rep(1, times = nrow(d)))

summary(fit_schoolfield_resp_nlsLM)
```

Boot strapping
```{r}
# bootstrap using case resampling
boot1 <- Boot(fit_schoolfield_resp_nlsLM, method = 'case')

#hist(boot1, layout = c(2,2))

boot1_preds <- boot1$t %>%
  as.data.frame() %>%
  drop_na() %>%
  mutate(iter = 1:n()) %>%
  group_by_all() %>%
  do(data.frame(T = seq(min(d$T-5), max(d$T+5), length.out = 100))) %>%
  ungroup() %>%
  mutate(pred = sharpeschoolfull_1981(temp = T, r_tref, e, el, tl, eh, th, tref = 20))

# calculate bootstrapped confidence intervals
boot1_conf_predsHnPp <- group_by(boot1_preds, T) %>%
  summarise(conf_lower = quantile(pred, 0.025),
            conf_upper = quantile(pred, 0.975)) %>%
  ungroup()

CI_HnPp<-boot1_conf_predsHnPp

# Predation prediction with bootstraping interval confidences
ggplot() +
  geom_line(aes(T-273, pred), newTHnPp, col = 'blue') +
  geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper), boot1_conf_predsHnPp, fill = 'blue', alpha = 0.3) +
  geom_point(aes(T-273, r), d, size = 1, alpha = 0.5, position="jitter") +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       y = 'Respiration rates',
       title = 'Growth rate with high nutrients and predation')+
  ylim(0, 9)

```

### Low nutrients and predation present (Schoolfield Model)
```{r}
d<-read.csv(file="exp1.csv", header=TRUE)
#d$Species=as.factor(d$Species)
str(d)
d$T<-d$Temp+273

d<-d%>%
  filter(Nutrients=="Low Nutrients" & Predation=="Yes")

start_vals <- get_start_vals(d$T, d$r, model_name = 'sharpeschoolfull_1981')

# fitting a lactin model
fit_schoolfield_resp<-nls_multstart(r~sharpeschoolfull_1981(temp = T, r_tref, e, el, tl, eh, th, tref = 20),
data = d,
iter = c(3,3,3,3,3,3),
start_lower = start_vals - 10,
start_upper = start_vals + 10,
lower = get_lower_lims(d$T, d$r, model_name = 'sharpeschoolfull_1981'),
upper = get_upper_lims(d$T, d$r, model_name = 'sharpeschoolfull_1981'),
supp_errors = 'Y',
convergence_count = FALSE) 

# Creating predictions
newT <- data.frame(T = seq(min(d$T-5), max(d$T+5), length.out=100))
newT$pred <- predict(fit_schoolfield_resp, newdata = newT)
newTLnPp<-newT

#summary of model and calculation parameters 
summary(fit_schoolfield_resp)

params<-rTPC::calc_params(fit_schoolfield_resp)
toptLnPp<-params$topt
params

fit_schoolfield_resp_nlsLM<-minpack.lm::nlsLM(r~sharpeschoolfull_1981(temp = T, r_tref, e, el, tl, eh, th, tref = 20), 
          data=d,
          start = coef(fit_schoolfield_resp), #I just add the coeficient from my previously calculated model 
                        lower = get_lower_lims(d$T, d$r, model_name = 'sharpeschoolfull_1981'),
                        upper = get_upper_lims(d$T, d$r, model_name = 'sharpeschoolfull_1981'),
                        weights = rep(1, times = nrow(d)))

summary(fit_schoolfield_resp_nlsLM)
```

Boot strapping
```{r}
# bootstrap using case resampling
boot1 <- Boot(fit_schoolfield_resp_nlsLM, method = 'case')

#hist(boot1, layout = c(2,2))

boot1_preds <- boot1$t %>%
  as.data.frame() %>%
  drop_na() %>%
  mutate(iter = 1:n()) %>%
  group_by_all() %>%
  do(data.frame(T = seq(min(d$T-5), max(d$T+5), length.out = 100))) %>%
  ungroup() %>%
  mutate(pred = sharpeschoolfull_1981(temp = T, r_tref, e, el, tl, eh, th, tref = 20))

# calculate bootstrapped confidence intervals
boot1_conf_predsLnPp <- group_by(boot1_preds, T) %>%
  summarise(conf_lower = quantile(pred, 0.025),
            conf_upper = quantile(pred, 0.975)) %>%
  ungroup()

CI_LnPp<-boot1_conf_predsLnPp

# Predation prediction with bootstraping interval confidences
ggplot() +
  geom_line(aes(T-273, pred), newTLnPp, col = 'blue') +
  geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper), boot1_conf_predsLn, fill = 'blue', alpha = 0.3) +
  geom_point(aes(T-273, r), d, size = 1, alpha = 0.5, position="jitter") +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       y = 'Respiration rates',
       title = 'Growth rate with low nutrients and predation present')+
  ylim(0, 9)

```

### TPCs Combining nutrients predation
```{r}
d<-read.csv(file="exp1.csv", header=TRUE)

ggplot() +
  geom_line(aes(T-273, pred), newTHn, col = '#00A087FF', size=0.7) +
  geom_line(aes(T-273, pred), newTLn, col = '#F39B7FB2', size=0.7) +
  geom_line(aes(T-273, pred), newTHnPp, col = 'darkgreen', size=0.7) +
  geom_line(aes(T-273, pred), newTLnPp, col = 'lightsalmon4', size=0.7) +
  geom_point(aes(Temp, r, color=Nutrients, shape=Predation), d, size = 1.5, alpha = 0.5, position="jitter")+         
  geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper), CI_Hn, fill = '#00A087FF', alpha = 0.2) +
  geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper),CI_Ln, fill = '#F39B7FB2', alpha = 0.2) +
  geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper), CI_HnPp, fill = 'darkgreen', alpha = 0.2) +
  geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper),CI_LnPp, fill = 'lightsalmon4', alpha = 0.2) +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       y = 'Growth rate (r)')+
  scale_y_continuous(limits=c(-0.2, 9))+
scale_x_continuous(limits=c(10, 38), breaks=seq(10, 38, 2))+
  theme(legend.position = c(0.15, 0.75),
         legend.key.spacing.y = unit(0.5, "cm"),
         legend.text = element_text(size = 12),
         panel.grid.major = element_blank(), 
         panel.grid.minor = element_blank(), 
         panel.background = element_rect(colour="white"), 
         panel.border = element_blank(),
         axis.line = element_line(colour = "black"),
         #axis.line.x.top = element_line(colour="black"),
         #axis.line.y.right = element_line(colour="black"),
         #axis.line.y.left = element_line(colour="black"),
         strip.background=element_rect(colour="white", fill="white"),
         strip.text = element_text(face = "italic", 
                                   color = "black", size = 13, hjust =0.05))+
          scale_colour_manual(name = "", 
 values =c('High Nutrients'="#00A087FF", 'Low Nutrients'="#F39B7FB2"), 
 labels= c('High Nutrients'="High Nutrients", 'Low Nutrients'="Low Nutrients"))+
  geom_vline(xintercept=toptHn-273, linetype="dashed", size=0.5, color="#00A087FF")+
  geom_vline(xintercept=toptLn-273, linetype="dashed", size=0.5, color="#F39B7FB2")+
  geom_vline(xintercept=toptHnPp-273, linetype="dashed", size=0.5, color="darkgreen")+
  geom_vline(xintercept=toptLnPp-273, linetype="dashed", size=0.5, color="lightsalmon4")


ggsave("TPC_combined_schoolfield.png", height = 12, width = 20, units = 'cm', dpi= 300, type = "cairo")
```

```{r}
d<-read.csv(file="exp1.csv", header=TRUE)
str(d)

ggplot() +
  geom_line(aes(T-273, pred), newTHn, col = '#00A087FF', size=0.7) +
  geom_line(aes(T-273, pred), newTLn, col = '#F39B7FB2', size=0.7) +
  geom_line(aes(T-273, pred), newTHnPp, col = 'darkgreen', size=0.7) +
  geom_line(aes(T-273, pred), newTLnPp, col = 'lightsalmon4', size=0.7) +
  geom_point(aes(Temp, r, color=Cat), d, size = 1.5, alpha = 0.5)+ 
  #position="jitter"        
  geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper), CI_Hn, fill = '#00A087FF', alpha = 0.2) +
  geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper),CI_Ln, fill = '#F39B7FB2', alpha = 0.2) +
  geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper), CI_HnPp, fill = 'darkgreen', alpha = 0.2) +
  geom_ribbon(aes(T-273, ymin = conf_lower, ymax = conf_upper),CI_LnPp, fill = 'lightsalmon4', alpha = 0.2) +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       y = 'Growth rate (r)')+
  scale_y_continuous(limits=c(-0.05, 9))+
scale_x_continuous(limits=c(10, 38), breaks=seq(10, 38, 2))+
  theme(legend.position = c(0.17, 0.75),
         legend.key.spacing.y = unit(0.3, "cm"),
         legend.text = element_text(size = 10.5),
         panel.grid.major = element_blank(), 
         panel.grid.minor = element_blank(), 
         panel.background = element_rect(colour="white"), 
         panel.border = element_blank(),
         axis.line = element_line(colour = "black"),
         #axis.line.x.top = element_line(colour="black"),
         #axis.line.y.right = element_line(colour="black"),
         #axis.line.y.left = element_line(colour="black"),
         strip.background=element_rect(colour="white", fill="white"),
         strip.text = element_text(face = "italic", 
                                   color = "black", size = 13, hjust =0.05))+
          scale_colour_manual(name = "", 
 values =c('High NutrientsNo'="#00A087FF", 'High NutrientsYes'="darkgreen", 'Low NutrientsNo'="#F39B7FB2", 'Low NutrientsYes'="lightsalmon4"), 
 labels= c('High NutrientsNo'="High Nutrients/No predation", 'Low NutrientsNo'="Low Nutrients/No predation", 'High NutrientsYes'="High Nutrients/Predation", 'Low NutrientsYes'="Low Nutrients/Predation"))+
  geom_vline(xintercept=toptHn-273, linetype="dashed", size=0.5, color="#00A087FF")+
  geom_vline(xintercept=toptLn-273, linetype="dashed", size=0.5, color="#F39B7FB2")+
  geom_vline(xintercept=toptHnPp-273, linetype="dashed", size=0.5, color="darkgreen")+
  geom_vline(xintercept=toptLnPp-273, linetype="dashed", size=0.5, color="lightsalmon4")

ggsave("TTPC_combined_schoolfield2.png", height = 13, width = 20, units = 'cm', dpi= 300, type = "cairo")
```


### Single curve considering all levels factor plus mean abundance and r
```{r}
d<-read.csv(file="exp1.csv", header=TRUE)
#d$Species=as.factor(d$Species)
str(d)
d$T<-d$Temp+273


start_vals <- get_start_vals(d$T, d$r, model_name = 'sharpeschoolfull_1981')

# fitting a lactin model
fit_schoolfield_resp<-nls_multstart(r~sharpeschoolfull_1981(temp = T, r_tref, e, el, tl, eh, th, tref = 20),
data = d,
iter = c(3,3,3,3,3,3),
start_lower = start_vals - 10,
start_upper = start_vals + 10,
lower = get_lower_lims(d$T, d$r, model_name = 'sharpeschoolfull_1981'),
upper = get_upper_lims(d$T, d$r, model_name = 'sharpeschoolfull_1981'),
supp_errors = 'Y',
convergence_count = FALSE) 

# Creating predictions
newT <- data.frame(T = seq(min(d$T-5), max(d$T+5), length.out=100))
newT$pred <- predict(fit_schoolfield_resp, newdata = newT)
#newTHnPp<-newT

#summary of model and calculation parameters 
summary(fit_schoolfield_resp)

params<-rTPC::calc_params(fit_schoolfield_resp)
topt<-params$topt
params


fit_schoolfield_resp_nlsLM<-minpack.lm::nlsLM(r~sharpeschoolfull_1981(temp = T, r_tref, e, el, tl, eh, th, tref = 20), 
          data=d,
          start = coef(fit_schoolfield_resp), #I just add the coeficient from my previously calculated model 
                        lower = get_lower_lims(d$T, d$r, model_name = 'sharpeschoolfull_1981'),
                        upper = get_upper_lims(d$T, d$r, model_name = 'sharpeschoolfull_1981'),
                        weights = rep(1, times = nrow(d)))

summary(fit_schoolfield_resp_nlsLM)
```
### Population growth with TPC
```{r}
d<-read.csv(file="exp1.csv", header=TRUE)

sum_pred<-d %>%
  group_by(Temp, Nutrients, Predation) %>%
  summarise(mean=mean(Cells), sd=sd(Cells), mean_r=mean(r), sd_r=sd(r), #summarizing abundance 
            n=n()) %>% #summarizing richness
  mutate(se=sd/sqrt(n), se_r=sd_r/sqrt(n))


# effect nutrients and predaton on TPC
r<-ggplot() +
   geom_point(data=sum_pred, aes(x=Temp, y=mean_r, color=Nutrients, shape=Predation, group = interaction(Nutrients, Predation)), 
             size = 2.5, position = pd)+
  geom_errorbar(data=sum_pred, aes(x=Temp, ymin=mean_r-se_r, ymax=mean_r+se_r, group = interaction(Nutrients, Predation), color=Nutrients),  
               size = 0.6, width = 0.2, alpha = 0.6, position = pd)+
    geom_point(data=data, aes(x=Temp, y=r, color=Nutrients, shape=Predation, group = interaction(Nutrients, Predation)),
               size = 1, position = pd, alpha=0.2)+
  geom_line(aes(T-273, pred), newT, col = '#00A087FF', size=2, alpha=0.2) +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       y = 'Growth rate (r)')+
  scale_y_continuous(limits=c(-0.05, 9))+
scale_x_continuous(limits=c(10, 38), breaks=seq(10, 38, 2))+
  theme(legend.position = c(0.17, 0.75),
    #legend.position = "none",
         legend.key.spacing.y = unit(0.1, "cm"),
         legend.text = element_text(size = 10),
         axis.title.x =element_blank(),
        axis.text.x=element_blank(),
      #  axis.ticks.x = element_blank(),
         panel.grid.major = element_blank(), 
         panel.grid.minor = element_blank(), 
         panel.background = element_rect(colour="white"), 
         panel.border = element_blank(),
         axis.line = element_line(colour = "black"),
         strip.background=element_rect(colour="white", fill="white"),
         strip.text = element_text(face = "italic", 
                                  color = "black", size = 13, hjust =0.05))+
    scale_colour_manual(values = c("High Nutrients"="#D55E00", "Low Nutrients"="#0072B2")) 

r
```

## Using gaussian for abundance 
```{r}

d<-read.csv(file="exp1.csv", header=TRUE)
#d$Species=as.factor(d$Species)
str(d)
d$T<-d$Temp+273


start_vals <- get_start_vals(d$T, d$Cells, model_name = 'gaussian_1987')

# fit model
mod <- nls.multstart::nls_multstart(Cells~gaussian_1987(temp = T,rmax, topt,a),
data = d,
iter = c(4,4,4),
start_lower = start_vals - 10,
start_upper = start_vals + 10,
lower = get_lower_lims(d$T, d$Cells, model_name = 'gaussian_1987'),
upper = get_upper_lims(d$T, d$Cells, model_name = 'gaussian_1987'),
supp_errors = 'Y',
convergence_count = FALSE)

# Creating predictions
newT_abund <- data.frame(T = seq(min(d$T-5), max(d$T+5), length.out=100))
newT_abund$pred <- predict(mod, newdata = newT_abund)

#newTHnPp<-newT
```
### Abundance plot with TPC
```{r}
abund<-ggplot() +
   geom_point(data=sum_pred, aes(x=Temp, y=mean, color=Nutrients, shape=Predation, group = interaction(Nutrients, Predation)), 
             size = 2.5, position = pd)+
  geom_errorbar(data=sum_pred, aes(x=Temp, ymin=mean-se, ymax=mean+se, group = interaction(Nutrients, Predation), color=Nutrients),  
               size = 0.6, width = 0.2, alpha = 0.6, position = pd)+
    geom_point(data=data, aes(x=Temp, y=Cells, color=Nutrients, shape=Predation, group = interaction(Nutrients, Predation)),
               size = 1, position = pd, alpha=0.2)+
  geom_line(aes(T-273, pred), newT_abund, col = "#00A087FF", size=2, alpha=0.2) +
  theme_bw(base_size = 12) +
  labs(x = 'Temperature (ºC)',
       y = 'Cells abundance')+
  scale_y_continuous(limits=c(0, 2000))+
scale_x_continuous(limits=c(10, 38), breaks=seq(10, 38, 2))+
  theme(#legend.position = c(0.17, 0.55),
    legend.position = "none",
         legend.key.spacing.y = unit(0.3, "cm"),
         legend.text = element_text(size = 10.5),
         panel.grid.major = element_blank(), 
         panel.grid.minor = element_blank(), 
         panel.background = element_rect(colour="white"), 
         panel.border = element_blank(),
         axis.line = element_line(colour = "black"),
         strip.background=element_rect(colour="white", fill="white"),
         strip.text = element_text(face = "italic", 
                                  color = "black", size = 13, hjust =0.05))+
    scale_colour_manual(values = c("High Nutrients"="#D55E00", "Low Nutrients"="#0072B2")) 

abund
```
###Putting together abundance and r
```{r}
#install.packages("patchwork")
library(patchwork)

fig1<-r/abund+plot_layout(heights = c(0.9, 1))
fig1
ggsave("Fig_1_TPC_r_abund.png", height = 22, width = 18, units = 'cm', dpi= 300, type = "cairo")
```


### TPCs
d <- data %>%
  mutate(temp_K = Temp + 273.15)

head(d)

tref <- 273.15 + 20


fit_pawar_ind <- function(d, min_n = 3) {
  
  if (nrow(d) < min_n) return(NULL)
  
  tryCatch(
    nls_multstart(
      r ~ pawar_2018(
        temp = temp_K,
        r_tref,
        e,
        eh,
        th,
        tref = tref
      ),
      data = d,
      iter = c(4, 4, 4, 4),
      start_lower = c(
        r_tref = min(d$r),
        e  = 0.2,
        eh = 0.5,
        th = 280
      ),
      start_upper = c(
        r_tref = max(d$r),
        e  = 1.5,
        eh = 5,
        th = 330
      ),
      supp_errors = "Y"
    ),
    error = function(e) NULL
  )
}


fits_ind <- d %>%
  group_by(Nutrients, Predation) %>%
  group_modify(~{
    tibble(
      pawar = list(fit_pawar_ind(.x))
    )
  }) %>%
  ungroup()



fit_pawar_replica <- function(d) {
  
  if (nrow(d) < 6) return(NULL)
  
  tryCatch(
    nls_multstart(
      r ~ pawar_2018(
        temp = T,
        r_tref,
        e,
        eh,
        topt,
        tref = 20
      ),
      data = d,
      iter = c(3, 3, 3, 3),
      start_lower = get_start_vals(d$T, d$rate, "pawar_2018") - 10,
      start_upper = get_start_vals(d$T, d$rate, "pawar_2018") + 10,
      lower = get_lower_lims(d$T, d$rate, "pawar_2018"),
      upper = get_upper_lims(d$T, d$rate, "pawar_2018"),
      supp_errors = "Y",
      convergence_count = FALSE
    ),
    error = function(e) NULL
  )
}

#### 
get_topt_safe <- function(fit) {
  if (is.null(fit)) return(NA_real_)
  
  tryCatch(
    get_topt(fit, model_name = "pawar_2018"),
    error = function(e) NA_real_
  )
}

topt_ind <- fits_ind %>%
  mutate(
    topt_K = map_dbl(pawar, get_topt_safe),
    topt_C = topt_K - 273.15
  )

topt_tret <- topt_ind %>%
  group_by(Nutrients, Predation) %>%
  summarise(
    n_ind = sum(!is.na(topt_C)),
    mean_topt = mean(topt_C, na.rm = TRUE),
    sd_topt   = sd(topt_C, na.rm = TRUE),
    se_topt   = sd_topt / sqrt(n_ind),
    .groups = "drop"
  )

